---
title: "02_main"
output: html_document
date: "2026-10-07"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath(".."))
```

## Import data and packages

```{r import}

# 1. Packages

library(rnaturalearth)
library(sf)
library(raster)
library(ggplotify)
library(ggspatial)
library(ggrepel)
library(plyr)
library(dagitty)
library(ggdag)
library(ggpubr)
library(scales)
library(simcausal)
library(MixSIAR)
library(tidybayes)
library(brms)
library(grid)
library(gridExtra)
library(magick)
library(cowplot)
library(tidyverse)
library(piecewiseSEM)
library(reshape2)
library(jtools)
library(modelr)
library(lme4)

# 2. Data

# Site data

site_data <- read.csv("data/CHA23_Site_info.csv")
sb_data <- read.csv("data/Seabird_island_data.csv")
island_data <- read.csv("data/CHA23_Source_sites.csv")

plankton_site_data <- read.csv("data/Plankton_Site_data.csv")
plank_site_data <- read.csv("data/Plank_Site_data.csv") #Southampton
coral_site_data <- read.csv("data/Acropora_Site_data.csv")
chaetrif_site_data <- read.csv("data/Butterflyfish_Site_data.csv")

# SIA data

turf_SIA <- read.csv("data/CHA23_SIA_data.csv") %>% filter(Taxon == "Turf") %>% 
  mutate(Site_ID = str_sub(ID, 1, 2),
         Sample_ID = str_sub(ID, 3)) %>% 
  left_join(island_data, by = c("Site_ID")) %>% 
  left_join(sb_data, by = c("Island", "Atoll")) %>% 
  select(Taxon, N15, C13, Seabird_Biomass_density_prop, Atoll, Island, Year)

det_SIA <- read.csv("data/CHA23_SIA_data.csv") %>% filter(Taxon == "Detritus") %>% 
  mutate(Site_ID = str_sub(ID, 1, 2),
         Sample_ID = str_sub(ID, 3)) %>% 
  left_join(island_data, by = c("Site_ID")) %>% 
  left_join(sb_data, by = c("Island", "Atoll")) %>% 
  select(Taxon, N15, C13, Seabird_Biomass_density_prop, Atoll, Island, Year)

zoop_SIA <- read.csv("data/CHA23_SIA_data.csv") %>% filter(Taxon == "Zooplankton") %>% 
  left_join(plankton_site_data, by = c("ID" = "Sample_ID"))  %>% 
  left_join(sb_data, by = c("Island", "Atoll")) %>% 
  select(Taxon, N15, C13, Seabird_Biomass_density_prop, Atoll, Island, Year)

pom_SIA <- read.csv("data/CHA23_SIA_data.csv") %>% filter(Taxon == "POM") %>% 
  left_join(plankton_site_data, by = c("ID" = "Sample_ID"))  %>% 
  left_join(sb_data, by = c("Island", "Atoll")) %>% 
  select(Taxon, N15, C13, Seabird_Biomass_density_prop, Atoll, Island, Year)

chaetrif_det_SIA <- read.csv("data/CHA23_SIA_data.csv") %>% filter(Taxon == "Chaetrif_detritus") %>% 
  left_join(chaetrif_site_data, by = c("ID" = "Sample_ID"))  %>% 
  left_join(sb_data, by = c("Island", "Atoll")) %>% 
  select(Taxon, N15, C13, Seabird_Biomass_density_prop, Atoll, Island, Year)

coral_SIA <- read.csv("data/CHA23_SIA_data.csv") %>% filter(Taxon == "Coral") %>% 
  left_join(coral_site_data, by = c("ID" = "Sample_ID"))  %>% 
  left_join(sb_data, by = c("Island", "Atoll")) %>% 
  select(Taxon, N15, C13, Seabird_Biomass_density_prop, Atoll, Island, Year)

symbiont_SIA <- read.csv("data/CHA23_SIA_data.csv") %>% filter(Taxon == "Symbiont") %>% 
  left_join(coral_site_data, by = c("ID" = "Sample_ID"))  %>% 
  left_join(sb_data, by = c("Island", "Atoll")) %>% 
  select(Taxon, N15, C13, Seabird_Biomass_density_prop, Atoll, Island, Year)

plank_day_SIA <- read.csv("data/CHA23_SIA_data.csv") %>% filter(Taxon == "Plank_day") %>% 
  left_join(plank_site_data, by = c("ID" = "Sample_ID"))  %>% 
  left_join(sb_data, by = c("Island", "Atoll")) %>% 
  select(Taxon, N15, C13, Seabird_Biomass_density_prop, Atoll, Island, Year)

plank_night_SIA <- read.csv("data/CHA23_SIA_data.csv") %>% filter(Taxon == "Plank_night") %>% 
  left_join(plank_site_data, by = c("ID" = "Sample_ID"))  %>% 
  left_join(sb_data, by = c("Island", "Atoll")) %>% 
  select(Taxon, N15, C13, Seabird_Biomass_density_prop, Atoll, Island, Year)

plankton_SIA <- bind_rows(plank_day_SIA, zoop_SIA) %>% 
  mutate(Taxon = "Plankton") 

conv_factors <- read.csv("data/Conversion_factors.csv")

invert_data <- read.csv("data/CHA23_Invert_data.csv") %>% 
  left_join(site_data, by = c("Site" = "ID")) %>% 
  left_join(sb_data, by = c("Island", "Atoll")) %>% 
  mutate(r = CSL/pi, Area = (2*pi*r^2)/10000) %>% 
  filter(Condition == "ok") %>% 
  left_join(conv_factors, by = "FAM") %>% 
  mutate(AFDM = W*Mean)

crypto_fish_data <- read.csv("data/CHA23_Fish_data.csv") %>% 
  left_join(site_data, by = c("Site" = "ID")) %>% 
  left_join(sb_data, by = c("Atoll", "Island")) %>% 
  filter(FAM %in% c("Gobiidae", "Blenniidae", "Gobiesocidae", "Tripterygiidae", 
                    "Syngnathidae", "Pseudochromidae","Plesiopidae", "Apogonidae", "Callionymidae")) %>% 
  mutate(r = CSL/pi, Area = (2*pi*r^2)/10000) %>% 
  mutate(TL = TL/10) %>% #mm to cm
  filter(GENSPE != "Chlidichthys chagosensis") %>%
  filter(Condition == "ok")   

inv_crypto_fish_data <- read.csv("data/CHA23_Fish_data.csv") %>% 
  left_join(site_data, by = c("Site" = "ID")) %>% 
  left_join(sb_data, by = c("Atoll", "Island")) %>% 
  filter(FAM %in% c("Pseudochromidae")) %>% 
  mutate(r = CSL/pi, Area = (2*pi*r^2)/10000) %>% 
  mutate(TL = TL/10) %>% #mm to cm
  filter(GENSPE == "Chlidichthys chagosensis") %>%
  filter(Condition == "ok")  

mediators_nutrients <- bind_rows(plank_day_SIA, 
                                 zoop_SIA,
                                 turf_SIA, 
                                 det_SIA, 
                                 pom_SIA, 
                                 chaetrif_det_SIA, 
                                 coral_SIA, symbiont_SIA, 
                                 plankton_SIA, plank_night_SIA)

mediators_nutrients_wide <- mediators_nutrients %>% 
  select(-C13, -Year) %>% 
  group_by(across(c("Atoll", "Island")), Group = Taxon) %>%
  summarise(d15N_mean = mean(N15, na.rm = TRUE),
    .groups = "drop") %>%
  pivot_wider(names_from  = Group,
    values_from = c(d15N_mean),
    names_prefix = "N15_",
    names_sep   = "_")

# quantify inter-lab variation

set.seed(27)

mediators_nutrients_lab <- mediators_nutrients %>%
  mutate(
    Lab = case_when(
      Taxon %in% c("Turf", "Detritus") ~ "Texas",
      Taxon %in% c("Plank_day", "Plank_night", "Chaetrif_detritus") ~ "Lancaster",
      Taxon %in% c("Coral", "Symbiont") ~ "Southampton",
      Taxon %in% c("POM", "Zooplankton") ~ "New Mexico",
      TRUE ~ NA_character_)) %>% 
  filter(!is.na(Lab)) 

dat_test_var_n15 <- mediators_nutrients_lab %>%
  filter(!is.na(N15), !is.na(Taxon), !is.na(Lab), !is.na(Island))

m_var_nested <- brm(N15 ~ 1 + (1|Lab/Taxon) + (1|Island), data = dat_test_var_n15, iter = 4000, control = list(adapt_delta = 0.99, max_treedepth = 15))

VarCorr(m_var_nested)
performance::icc(m_var_nested)

# UVC

uvc_raw <- read.csv("data/CHA23_UVC_data.csv") 

# egestion data

load("data/cnpflux_output.Rdata")

egestion_dat <- cnpflux %>% 
  filter(Diet == "Planktivore" | Diet == "Herbivore" | Diet == "Corallivore") %>% 
  group_by(Island, Atoll, Transect, Year) %>% 
  mutate(Wc = sum(Wc_mean, na.rm = T)/Area,
         Wp = sum(Wp_mean, na.rm = T)/Area,
         Wn = sum(Wn_mean, na.rm = T)/Area,
         Fn = sum(Fn_mean, na.rm = T)/Area,
         Fp = sum(Fp_mean, na.rm = T)/Area) %>% 
  left_join(sb_data, by = c("Atoll", "Island")) %>% 
  distinct(Wc, Wn, Wp, Fp, Fn, Island, Atoll, Transect, Year, Seabird_Biomass_density_prop)

egestion_dat_island <- egestion_dat %>% 
  group_by(Island, Atoll) %>% 
  summarize(Wc = mean(Wc))

# Planktivores, herbivores and corallivores contribute to 2/3 of detritus production so likely appropriate proxies
  
egestion_dat_tot <- cnpflux %>% 
  group_by(Island, Atoll, Transect, Year, Diet) %>% 
  group_by(Diet) %>% 
  mutate(Wc = sum(Wc_mean, na.rm = T)) %>% 
  distinct(Wc, Diet)

sum(egestion_dat_tot$Wc) #668.6848
#439.679702/668.6848

# coral growth data

coral_growth_dat <- read.csv("data/Acropora_SIA_Growth.csv") %>% 
  select(Atoll, Island, Host_N15, Symbiont_N15, diff_SA_year) %>% 
  rename(Growth = diff_SA_year) %>% 
  left_join(mediators_nutrients_wide, by = c("Atoll", "Island")) %>% # discrepancy in symbiont N15 values is because the one from mediators nutrients wide df is an average per island, and the one from the growth dataset is coral-specific 
  left_join(sb_data, by = c("Atoll", "Island"))

# Silhouettes

img_herb <- image_read("figures/silhouettes/img_herb.png") %>% 
  image_background("none") %>%
  image_flatten() %>% as.raster() %>% 
  rasterGrob(interpolate = T)

img_plank <- image_read("figures/silhouettes/img_plank.png") %>% 
  image_background("none") %>%
  image_flatten() %>% as.raster() %>% 
  rasterGrob(interpolate = T)

img_cor <- image_read("figures/silhouettes/img_cor.png") %>% 
  image_background("none") %>%
  image_flatten() %>% as.raster() %>% 
  rasterGrob(interpolate = T)

img_det <- image_read("figures/silhouettes/img_det.png") %>% 
  image_background("none") %>%
  image_flatten() %>% as.raster() %>% 
  rasterGrob(interpolate = T)

img_omni <- image_read("figures/silhouettes/img_omni.png") %>% 
  image_background("none") %>%
  image_flatten() %>% as.raster() %>% 
  rasterGrob(interpolate = T)

img_carn <- image_read("figures/silhouettes/img_carn.png") %>% 
  image_background("none") %>%
  image_flatten() %>% as.raster() %>% 
  rasterGrob(interpolate = T)

img_inv <- image_read("figures/silhouettes/img_inv.png") %>% 
  image_background("none") %>%
  image_flatten() %>% as.raster() %>% 
  rasterGrob(interpolate = T)

img_pisc <- image_read("figures/silhouettes/img_pisc.png") %>%
  image_background("none") %>%
  image_flatten() %>% as.raster() %>% 
  rasterGrob(interpolate = T)

img_det_n15 <- image_read("figures/silhouettes/img_det_n15.png") %>% 
  image_flatten() %>% as.raster() %>% 
  rasterGrob(interpolate = T)

img_turf_n15 <- image_read("figures/silhouettes/img_turf_n15.png") %>% 
  image_flatten() %>% as.raster() %>% 
  rasterGrob(interpolate = T)

img_pom_n15 <- image_read("figures/silhouettes/img_pom_n15.png") %>% 
  image_flatten() %>% as.raster() %>% 
  rasterGrob(interpolate = T)

img_symbiont_n15 <- image_read("figures/silhouettes/img_symbiont_n15.png") %>% 
  image_flatten() %>% as.raster() %>% 
  rasterGrob(interpolate = T)

img_inv_prod <- image_read("figures/silhouettes/img_inv_prod.png") %>% 
  image_flatten() %>% as.raster() %>% 
  rasterGrob(interpolate = T)

img_fish_prod <- image_read("figures/silhouettes/img_fish_prod.png") %>% 
  image_flatten() %>% as.raster() %>% 
  rasterGrob(interpolate = T)

img_det_prod <- image_read("figures/silhouettes/img_det_prod.png") %>% 
  image_flatten() %>% as.raster() %>% 
  rasterGrob(interpolate = T)

img_coral_prod <- image_read("figures/silhouettes/img_coral_prod.png") %>% 
  image_flatten() %>% as.raster() %>% 
  rasterGrob(interpolate = T)


```


# Map

```{r plot-figs1}

sb_gps <- read.csv("data/GPS.csv")

sf::sf_use_s2(FALSE)

# 1. IO map ----

worldmap <- ne_countries(scale = 10, returnclass = 'sf')
countries <- ne_download(category = "cultural", type = "countries", 
                         returnclass = "sf", scale = 110) 
ocean <- st_as_sfc(st_bbox(worldmap)) %>%
  st_difference(st_union(countries))

ioshp <- read_sf("data/map/ne_10m_land.shp", stringsAsFactors = TRUE)

ocean_cropped_IO <- st_crop(ocean, xmin = 35, xmax = 80, ymin = -29, ymax = 9)

CP_IO <- as(extent(35, 80, -29, 9), "SpatialPolygons")
proj4string(CP_IO) <- CRS(proj4string(as_Spatial(ioshp)))
out_IO <- st_intersection(st_as_sf(ioshp), st_as_sf(CP_IO), byid = TRUE)

map_IO <- ggplot() + 
  theme_bw() +
  coord_map() + 
  geom_sf(data = ocean_cropped_IO, fill = "white", col = "white") +
  geom_sf(data = out_IO, fill = "lightgrey") +
  geom_sf(data = out_IO, fill = "transparent") +
  annotate(geom = "text", x = 65, y = -15, label = "Indian Ocean", 
           fontface = "italic", color = "darkgrey", size = 2.7) +
  geom_rect(data = out_IO, xmin = 71, xmax = 73, ymin = -6.5, ymax = -5.1, fill = NA, colour = "#474F58", 
            linewidth = 0.5) +
  annotation_scale(data = out_IO, location = "bl", width_hint = 0.05, height = unit(0.2, "cm"), text_cex = 0.5, text_pad = unit(0.15, "cm")) +
  guides(x = guide_axis(position = "top")) +
  theme(legend.margin = margin(), legend.title = element_text(hjust = 0, size = 9),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        panel.grid = element_blank()) 

map_IO

# 2. Chagos map ----

chashp <- read_sf("data/map/Chagos_v6.shp", stringsAsFactors = TRUE)

ocean_cropped_C <- st_crop(ocean, xmin = 71, xmax = 73, ymin = -6.5, ymax = -5.1)

CP_C <- as(extent(70, 74.2, -6.5, -5.1), "SpatialPolygons")
proj4string(CP_C) <- CRS(proj4string(as_Spatial(chashp)))
out_C <- st_intersection(st_as_sf(chashp), st_as_sf(CP_C), byid = TRUE)


map_C <- ggplot() +
  theme_bw() +
  geom_point(data = sb_gps, aes(y = Lat, x = Lon, fill = log(Seabird_density)), 
             size = 3, col = "black", shape = 21) +
  coord_map() + 
  geom_sf(data = ocean_cropped_C, fill = "white", col = "white") +
  geom_sf(data = out_C, fill = "grey96") +
  geom_sf(data = out_C, fill = "transparent") +
  geom_rect(data = out_C, xmin = 72.182, xmax = 72.292, ymin = -5.372, ymax = -5.272, fill = NA, colour = "#474F58", 
            linewidth = 0.5) +
  geom_rect(data = out_C, xmin = 71.696, xmax = 72.006, ymin = -5.485, ymax = -5.175, fill = NA, colour = "#474F58", 
            linewidth = 0.5) +
  geom_rect(data = out_C, xmin = 71.306, xmax = 72.33, ymin = -6.250, ymax = -5.65, fill = NA, colour = "#474F58",
            linewidth = 0.5) +
  annotation_scale(data = out_C, location = "tl", width_hint = 0.05, height = unit(0.2, "cm"), text_cex = 0.5, 
                   text_pad = unit(0.15, "cm")) +
  scale_fill_gradient(high = "#1D9BF0", low = "#E63946", name = "Log-Seabird\nbiomass\n(kg ha⁻¹)") +
  theme(legend.title = element_text(size = 8, lineheight = 1),
        legend.text = element_text(size = 8),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        panel.grid = element_blank(),
        plot.margin = margin(0.5, 0, 0, 0, "cm")) +
  scale_x_continuous(breaks=seq(71.2, 72.8, 0.5))

# Salomon map

ocean_cropped_S <- st_crop(ocean, xmin = 72.182, xmax = 72.292, ymin = -5.372, ymax = -5.262)

CP_S <- as(extent(72.182, 72.292, -5.372, -5.262), "SpatialPolygons")
proj4string(CP_S) <- CRS(proj4string(as_Spatial(chashp)))
out_S <- st_intersection(st_as_sf(chashp), st_as_sf(CP_S), byid = TRUE)


map_S <- ggplot() +
  theme_bw() +
  coord_map() + 
  geom_sf(data = ocean_cropped_S, fill = "transparent", col = "white") +
  geom_sf(data = out_S, fill = "grey96") +
  geom_sf(data = out_S, fill = "transparent") +
  scale_fill_gradient(high = "#1D9BF0", low = "#E63946") +
  geom_point(data = sb_gps %>% filter(Atoll == "Salomon"), aes(y = Lat, x = Lon, fill = log(Seabird_density)), 
             size = 3, col = "black", shape = 21) +
  annotation_scale(data = out_S, location = "tl", width_hint = 0.12, height = unit(0.2, "cm"), 
                   text_cex = 0.5, text_pad = unit(0.15, "cm")) +
  annotate(geom = "text", x = 72.257, y = -5.294, label = "Ile de la Passe", 
           fontface = "italic", color = "#474F58", size = 2.7) +
  annotate(geom = "text", x = 72.204, y = -5.325, label = "Ile Anglaise", 
           fontface = "italic", color = "#474F58", size = 2.7) +
  annotate(geom = "text", x = 72.27, y = -5.36, label = "Ile Fouquet", 
           fontface = "italic", color = "#474F58", size = 2.7) +
  theme(legend.margin = margin(), legend.title = element_text(hjust = 0, size = 9),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        panel.grid = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"))

# Peros Banhos map

ocean_cropped_PB <- st_crop(ocean, xmin = 71.696, xmax = 72.006, ymin = -5.485, ymax = -5.175)

CP_PB <- as(extent(71.696, 72.006, -5.485, -5.175), "SpatialPolygons")
proj4string(CP_PB) <- CRS(proj4string(as_Spatial(chashp)))
out_PB <- st_intersection(st_as_sf(chashp), st_as_sf(CP_PB), byid = TRUE)


map_PB <- ggplot() +
  theme_bw() +
  coord_map() + 
  geom_sf(data = ocean_cropped_PB, fill = "transparent", col = "white") +
  geom_sf(data = out_PB, fill = "grey96") +
  geom_sf(data = out_PB, fill = "transparent") +
  scale_fill_gradient(high = "#1D9BF0", low = "#E63946") +
  geom_point(data = sb_gps %>% filter(Atoll == "Peros Banhos"), aes(y = Lat, x = Lon, fill = log(Seabird_density)), 
             size = 3, col = "black", shape = 21) +
  annotation_scale(data = out_PB, location = "tl", width_hint = 0.05, height = unit(0.2, "cm"), 
                   text_cex = 0.5, text_pad = unit(0.15, "cm")) +
  annotate(geom = "text", x = 71.968, y = -5.223, label = "Ile Yeye", 
           fontface = "italic", color = "#474F58", size = 2.7) +
  annotate(geom = "text", x = 71.73, y = -5.47, label = "Ile Anglaise", 
           fontface = "italic", color = "#474F58", size = 2.7) +
  annotate(geom = "text", x = 71.98, y = -5.425, label = "Grande \nIle \nCoquillage", 
           fontface = "italic", color = "#474F58", size = 2.7, lineheight = 0.8) +
  annotate(geom = "text", x = 71.875, y = -5.24, label = "Ile \nLongue", 
           fontface = "italic", color = "#474F58", size = 2.7, lineheight = 0.8) +
  annotate(geom = "text", x = 71.717, y = -5.41, label = "Ile \nPoule", 
           fontface = "italic", color = "#474F58", size = 2.7, lineheight = 0.8) +
  annotate(geom = "text", x = 71.717, y = -5.26, label = "Grande \nMapou", 
           fontface = "italic", color = "#474F58", size = 2.7, lineheight = 0.8) +
  theme(legend.margin = margin(), legend.title = element_text(hjust = 0, size = 9),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        panel.grid = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"))

# Great Chagos Bank map

ocean_cropped_GCB <- st_crop(ocean, xmin = 71.15, xmax = 72.33, ymin = -6.25, ymax = -5.4)

CP_GCB <- as(extent(71.15, 72.33, -6.25, -5.65), "SpatialPolygons")
proj4string(CP_GCB) <- CRS(proj4string(as_Spatial(chashp)))
out_GCB <- st_intersection(st_as_sf(chashp), st_as_sf(CP_GCB), byid = TRUE)


map_GCB <- ggplot() +
  theme_bw() +
  coord_map() + 
  geom_sf(data = ocean_cropped_GCB, fill = "transparent", col = "white") +
  geom_sf(data = out_GCB, fill = "grey96") +
  geom_sf(data = out_GCB, fill = "transparent") +
  geom_point(data = sb_gps %>% filter(Atoll == "Great Chagos Bank"), aes(y = Lat, x = Lon, fill = log(Seabird_density)), 
             size = 3, col = "black", shape = 21) +
  scale_fill_gradient(high = "#1D9BF0", low = "#E63946") +
  annotation_scale(data = out_GCB, location = "tl", width_hint = 0.1, height = unit(0.2, "cm"), 
                   text_cex = 0.5, text_pad = unit(0.15, "cm")) +
  annotate(geom = "text", x = 71.4, y = -6, label = "Middle \nBrother", 
           fontface = "italic", color = "#474F58", size = 2.7, lineheight = 0.8) +
  annotate(geom = "text", x = 71.4, y = -6.1, label = "South \nBrother", 
           fontface = "italic", color = "#474F58", size = 2.7, lineheight = 0.8) +
  annotate(geom = "text", x = 71.21, y = -6.154, label = "Eagle \nIsland", 
           fontface = "italic", color = "#474F58", size = 2.7, lineheight = 0.8) +
    annotate(geom = "text", x = 72.25, y = -5.6, label = "Nelson \nIsland", 
           fontface = "italic", color = "#474F58", size = 2.7, lineheight = 0.8) +
  theme(legend.margin = margin(), legend.title = element_text(hjust = 0, size = 9),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        panel.grid = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"))


map_GCB

map.plot <- ggarrange(
  ggarrange(map_IO, map_C + rremove("xy.text") + rremove("ticks"), nrow = 1),
  ggarrange(
  map_GCB + rremove("xy.text") + rremove("ticks") + rremove("legend"),
  map_PB + rremove("xy.text") + rremove("ticks") + rremove("legend"), 
  map_S + rremove("xy.text") + rremove("ticks") + rremove("legend"), 
  labels = c("Great Chagos \n           Bank", "Peros Banhos", "Salomon"), 
  hjust = c(-0.9, -0.9, -1.7), vjust = c(1.5, 2.2, 2.2), font.label = list(size = 10, color = "#474F58"),
  align = "h", nrow = 1),
 nrow = 2, heights = c(1.1, 1)) 

map.plot

map_grob <- as.grob(map.plot)

composite_with_arrows <- gTree(children = gList(
  map_grob,
  linesGrob(x = unit(c(0.58, 0.3), "npc"),
    y = unit(c(0.625, 0.475), "npc"),
    gp = gpar(col = "#474F58", lwd = 1.2)),
  linesGrob(x = unit(c(0.65, 0.62), "npc"),
    y = unit(c(0.795, 0.475), "npc"),
    gp = gpar(col = "#474F58", lwd = 1.2)),
  linesGrob(x = unit(c(0.73, 0.9), "npc"),
    y = unit(c(0.82, 0.475), "npc"),
    gp = gpar(col = "#474F58", lwd = 1.2)),
  linesGrob(x = unit(c(0.395, 0.505), "npc"),
    y = unit(c(0.766, 0.71), "npc"),
    gp = gpar(col = "#474F58", lwd = 1.2))
))

arrow_plot <- ggplot() + 
  theme_void() +
  annotation_custom(composite_with_arrows)

arrow_plot

#ggsave("figures/supp/FigS1.jpg", arrow_plot, width = 7, height = 5, units = "in", dpi = 600)
#ggsave("figures/supp/FigS1.pdf", arrow_plot, width = 6, height = 4, units = "in", dpi = 600)
```

# Calculate productivity of cryptobenthic fish and invertebrates

```{r prod-inv}

prod_inv_data <- invert_data %>% 
  filter(!is.na(AFDM)) %>% 
  mutate(Prod_indiv = 365*(10^(-2.31+0.8*log10(AFDM*10^6) + 0.89*log10(28)))/10^6,
         Prod = Prod_indiv/Area*10, #Edgar 1990 for marine/estuarine taxa; see formula in Fraser et al 2020. P is productivity of of individual in g AFDW d-1, now in kg.ha-1
         Biomass = W/Area*10)

prod_inv_data_site <- prod_inv_data %>%
  group_by(Site, Island, Atoll, Seabird_Biomass_density_prop) %>% 
  summarize(Prod = sum(Prod, na.rm = T),
            Biomass = sum(W, na.rm = T),
            Area = first(Area)) %>% 
  distinct(Prod, Biomass, Site, Island, Atoll)

prod_inv_data_island <- prod_inv_data_site %>%
  group_by(Island, Atoll) %>%
  summarise(
    Prod = mean(Prod, na.rm = T),
    Biomass = mean(Biomass, na.rm = T))

```

```{r prod-crypto-fish}

crypto_site_list <- crypto_fish_data %>% distinct(Site, Atoll, Island)

traits <- read.csv('data/fishtraits_productivity.csv') #from Brandl et al 2024 Ecology
kmax_list <- read.csv('data/All_Kmax_final.csv') %>% 
  mutate(Species = str_replace_all(Species, "_", " "))

sp_uvc_kmax <- merge(traits, kmax_list, by = c("MaxSizeTL","Diet", "Species"), all.x=TRUE)
sp_uvc_kmax_2 <- unique(sp_uvc_kmax) %>% select(-LW_a, -LW_b) 

bayes_ab <- read.csv("data/bayes_ab_crypto.csv") %>% rename(Species = species, LW_a = lwa_m, LW_b = lwb_m) %>% select(-lwa_sd, -lwb_sd)

crypto_fish.biomass.data_site <- crypto_fish_data %>% 
  filter(!is.na(TL)) %>% 
  filter(GENSPE != "Chlidichthys chagosensis") %>% 
  mutate(W_m = W/Area) %>% 
  group_by(Atoll, Island, Site, Depth, Seabird_Biomass_density_prop) %>% 
  mutate(Biomass = sum(as.numeric(W_m), na.rm = T)) %>% 
  distinct(Atoll, Island, Site, Biomass, Area, Depth, Seabird_Biomass_density_prop) 

crypto_fish.biomass.data_island <- crypto_fish.biomass.data_site %>%
  group_by(Atoll, Island, Seabird_Biomass_density_prop) %>%
  summarise(
    Biomass = mean(Biomass, na.rm = T),
    Depth = mean(Depth, na.rm = T),
    n_sites = n())

crypto_fish_dat_bio_wide_site <- crypto_fish_data %>% 
  rename(Species = GENSPE) %>% 
  filter(!is.na(TL)) %>% 
  filter(Species != "Chlidichthys chagosensis") %>% 
  group_by(Atoll, Island, Species, Site) %>% 
  summarize(Sum_Bio = sum(W/Area, na.rm = T)) %>% 
  pivot_wider(names_from = Species, values_from = Sum_Bio, values_fill = 0)

crypto_fish_dat_bio_wide_island <- crypto_fish_dat_bio_wide_site %>%
  group_by(Atoll, Island) %>%
  summarize(across(where(is.numeric), mean, na.rm = T))

#sum  biomass
crypto_fish_sum_bio_site <- rowSums(crypto_fish_dat_bio_wide_site[,4:ncol(crypto_fish_dat_bio_wide_site)])
crypto_fish_chagos_div_site <- cbind(crypto_fish_dat_bio_wide_site[1:3], Biomass = crypto_fish_sum_bio_site)

crypto_fish_sum_bio_island <- rowSums(crypto_fish_dat_bio_wide_island[,3:ncol(crypto_fish_dat_bio_wide_island)])
crypto_fish_chagos_div_island <- cbind(crypto_fish_dat_bio_wide_island[1:2], Biomass = crypto_fish_sum_bio_island)

#combine UVC data with kmax data

##add column for k values in fish data
crypto_fish_dat_k <- merge(crypto_fish_data %>% filter(!is.na(TL)) %>% filter(GENSPE != "Chlidichthys chagosensis") %>% 
                             rename(Species = GENSPE),sp_uvc_kmax_2, by=c("Species"), all.x=TRUE ) %>% filter(!is.na(Kmax))
crypto_fish_dat_k <- merge(crypto_fish_dat_k, bayes_ab, by = c("Species"))

crypto_fish_dat_k[crypto_fish_dat_k$TL>crypto_fish_dat_k$MaxSizeTL,] 

crypto_fish_dat_k$TL <- ifelse(
  crypto_fish_dat_k$TL > crypto_fish_dat_k$MaxSizeTL,
  crypto_fish_dat_k$MaxSizeTL,
  crypto_fish_dat_k$TL
)

crypto_fish_dat_prod <- crypto_fish_dat_k

#calculate prod
#Derived from Morais & Bellwood 2019

#check which species estimated length > max length 
crypto_fish_dat_k[crypto_fish_dat_k$TL>crypto_fish_dat_k$MaxSizeTL,] 

#calculate age
crypto_fish_dat_prod$EstAge<-(1/crypto_fish_dat_prod$Kmax)*log((crypto_fish_dat_prod$MaxSizeTL)/((1-crypto_fish_dat_prod$TL/crypto_fish_dat_prod$MaxSizeTL)*crypto_fish_dat_prod$MaxSizeTL))

#plug back age into VGBF to calculate growth
age <- (1:365) / 365

#set up table for new lengths: 1 column per day, 1 row per individual fish
crypto_fish_vb_len_tab <- matrix (ncol = length (age), nrow = nrow (crypto_fish_dat_prod), dimnames = list (NULL, paste ('Day', 1:365, sep="_")))

#for each individual, calculate new length for that day using VBGF formula (written above)
for (u in 1:nrow (crypto_fish_dat_prod)) {
  
  crypto_fish_vb_len_tab [u, ] <- crypto_fish_dat_prod$MaxSizeTL[u]*(1-exp(-crypto_fish_dat_prod$Kmax[u]*(crypto_fish_dat_prod$EstAge[u]+age))) 
  
}
##convert length to weight using a,b coefs
crypto_fish_vb_wt_tab <- apply (crypto_fish_vb_len_tab, 2, function (x) crypto_fish_dat_prod$LW_a * (x ^ crypto_fish_dat_prod$LW_b))

#create production table (in grams, weight) per day
crypto_fish_biomass_not_rounded_g <- (crypto_fish_dat_prod$LW_a*crypto_fish_dat_prod$TL^crypto_fish_dat_prod$LW_b)
crypto_fish_vb_wt_tab <- cbind(crypto_fish_biomass_not_rounded_g, crypto_fish_vb_wt_tab)
colnames(crypto_fish_vb_wt_tab)[1] <- "Day_0"
crypto_fish_vb_prod_wt_tab <- crypto_fish_vb_wt_tab

for (u in 2:ncol(crypto_fish_vb_prod_wt_tab))
  for (v in 1:nrow(crypto_fish_vb_prod_wt_tab)) {
    crypto_fish_vb_prod_wt_tab [v,u ] <- crypto_fish_vb_wt_tab[v,u]-crypto_fish_vb_wt_tab[v,(u-1)]
  }

crypto_fish_vb_prod_wt_tab2<-crypto_fish_vb_prod_wt_tab[,2:ncol(crypto_fish_vb_prod_wt_tab)]

#incorporate size-dependant mortality for net productivity

crypto_fish_dat_prod$logZyear<- (-0.0066-(0.279*log(crypto_fish_dat_prod$MaxSizeTL))+(0.6543*log(crypto_fish_dat_prod$Kmax))+(0.4634*log(28)))
crypto_fish_dat_prod$Zyear<-exp(crypto_fish_dat_prod$logZyear)

crypto_fish_dat_prod$Zday<-crypto_fish_dat_prod$Zyear/365

#calculate probability of survival
#probability of survival = exp(-zday)
crypto_fish_dat_prod$SurvivalDay<-exp(-crypto_fish_dat_prod$Zday)

#vector of daily survival probabilities for the year
crypto_fish_psurv_tab <- matrix (ncol = 365, nrow = nrow (crypto_fish_dat_prod), dimnames = list (NULL, paste ('Day', 1:365)))
for (u in 1:nrow (crypto_fish_dat_prod)) {
  crypto_fish_psurv_tab [u, ] <- exp(-crypto_fish_dat_prod$Zday[u]) 
}

#simulate mortality per day

crypto_fish_surv_outcome_day <- matrix (ncol = 365, nrow = nrow (crypto_fish_psurv_tab))

for (u in 1:nrow(crypto_fish_psurv_tab))
  for (v in 1:ncol(crypto_fish_psurv_tab)) {
    crypto_fish_surv_outcome_day [u,v ] <- rbern(1,prob= crypto_fish_psurv_tab[u,v])
  }

nrow(subset(crypto_fish_surv_outcome_day,rowSums(crypto_fish_surv_outcome_day)!=365))
nrow(subset(crypto_fish_surv_outcome_day,rowSums(crypto_fish_surv_outcome_day)==365)) 

##need to make it so once there is a zero in the row, every value after that is zero
zero_row_replace <- function(x){
  x[which(cumany(x==0))] <- 0
  return(x)
}

crypto_fish_surv_outcome_day2<-adply(crypto_fish_surv_outcome_day, 1, zero_row_replace)
crypto_fish_surv_outcome_day2<-dplyr::select(crypto_fish_surv_outcome_day2, -c(X1)) #remove first row, don't want that

nrow(subset(crypto_fish_surv_outcome_day2,rowSums(crypto_fish_surv_outcome_day2)!=365))
nrow(subset(crypto_fish_surv_outcome_day2,rowSums(crypto_fish_surv_outcome_day2)==365))

#multiply survival table*production table to get production estimates
crypto_fish_est_daily_prod_tab <- crypto_fish_surv_outcome_day2*crypto_fish_vb_prod_wt_tab2

#um daily production over the course of a year
crypto_fish_prod_year <- rowSums(crypto_fish_est_daily_prod_tab)

#final conversions and save above simulation
crypto_fish_dat_prod_final <- crypto_fish_dat_prod
crypto_fish_dat_prod_final$prod_year_g <- crypto_fish_prod_year

#convert to kg/ha
crypto_fish_dat_prod_final$prod_year_kg_h <- crypto_fish_dat_prod_final$prod_year_g/crypto_fish_dat_prod_final$Area*10

#for station-level prod analyses
crypto_fish.site.prod.data <- ddply(crypto_fish_dat_prod_final, c("Atoll", "Island", "Site"), summarise,
                  Prod = sum(prod_year_kg_h))

#combine with other data
crypto_fish_chagos_site_prod <- merge(crypto_fish_chagos_div_site, crypto_fish.site.prod.data, by = c("Atoll", "Island", "Site"), all.x=TRUE)

crypto_fish.site.prod.data <- crypto_fish.biomass.data_site %>% 
  select(-Biomass) %>% 
  left_join(crypto_fish_chagos_site_prod, by = c("Atoll", "Island", "Site"))

#for island-level prod analyses
crypto_fish.island.prod.data <- crypto_fish.site.prod.data %>%
  group_by(Atoll, Island) %>%
  summarise(Prod = mean(Prod, na.rm = T))

#combine with other data
crypto_fish_chagos_island_prod <- merge(crypto_fish_chagos_div_island, crypto_fish.island.prod.data, by = c("Atoll", "Island"), all.x = T)

crypto_fish.island.prod.data <- crypto_fish.biomass.data_island %>% 
  select(-Biomass) %>% 
  left_join(crypto_fish_chagos_island_prod, by = c("Atoll", "Island")) 

```

```{r prod-inv-crypto-fish}

inv_crypto_fish.biomass.data_site <- inv_crypto_fish_data %>% 
  filter(!is.na(TL)) %>% 
  mutate(W_m = W/Area) %>% 
  group_by(Atoll, Island, Site, Abundance, Density, Depth, Seabird_Biomass_density_prop) %>% 
  mutate(Biomass = sum(as.numeric(W_m), na.rm = T)) %>% 
  distinct(Atoll, Island, Site, Biomass, Area, Depth, Seabird_Biomass_density_prop) 

inv_crypto_fish.biomass.data_island <- inv_crypto_fish.biomass.data_site %>%
  group_by(Atoll, Island, Seabird_Biomass_density_prop) %>%
  summarise(Biomass = mean(Biomass, na.rm = T),
    Depth = mean(Depth, na.rm = T),
    n_sites = n())

inv_crypto_fish_dat_bio_wide_site <- inv_crypto_fish_data %>% 
  rename(Species = GENSPE) %>% 
  filter(!is.na(TL)) %>% 
  group_by(Atoll, Island, Species, Site) %>% 
  summarize(Sum_Bio = sum(W/Area, na.rm = T)) %>% 
  pivot_wider(names_from = Species, values_from = Sum_Bio, values_fill = 0)

inv_crypto_fish_dat_bio_wide_island <- inv_crypto_fish_dat_bio_wide_site %>%
  group_by(Atoll, Island) %>%
  summarize(across(where(is.numeric), mean, na.rm = T))

#sum  biomass
inv_crypto_fish_sum_bio_site <- rowSums(inv_crypto_fish_dat_bio_wide_site[,4:ncol(inv_crypto_fish_dat_bio_wide_site)])
inv_crypto_fish_chagos_div_site <- cbind(inv_crypto_fish_dat_bio_wide_site[1:3], Biomass = inv_crypto_fish_sum_bio_site)

inv_crypto_fish_sum_bio_island <- rowSums(inv_crypto_fish_dat_bio_wide_island[,3:ncol(inv_crypto_fish_dat_bio_wide_island)])
inv_crypto_fish_chagos_div_island <- cbind(inv_crypto_fish_dat_bio_wide_island[1:2], Biomass = inv_crypto_fish_sum_bio_island)

#combine UVC data with kmax data

##add column for k values in fish data
inv_crypto_fish_dat_k <- merge(inv_crypto_fish_data %>% filter(!is.na(TL)) %>% 
                             rename(Species = GENSPE),sp_uvc_kmax_2, by=c("Species"), all.x=TRUE ) %>% filter(!is.na(Kmax))
inv_crypto_fish_dat_k <- merge(inv_crypto_fish_dat_k, bayes_ab, by = c("Species"))

inv_crypto_fish_dat_k[inv_crypto_fish_dat_k$TL>inv_crypto_fish_dat_k$MaxSizeTL,] 

inv_crypto_fish_dat_k$TL <- ifelse(
  inv_crypto_fish_dat_k$TL > inv_crypto_fish_dat_k$MaxSizeTL,
  inv_crypto_fish_dat_k$MaxSizeTL,
  inv_crypto_fish_dat_k$TL)

inv_crypto_fish_dat_prod <- inv_crypto_fish_dat_k

#calculate prod
#Derived from Morais & Bellwood 2019

#check which species estimated length > max length 
inv_crypto_fish_dat_k[inv_crypto_fish_dat_k$TL>inv_crypto_fish_dat_k$MaxSizeTL,] 

#calculate age
inv_crypto_fish_dat_prod$EstAge<-(1/inv_crypto_fish_dat_prod$Kmax)*log((inv_crypto_fish_dat_prod$MaxSizeTL)/((1-inv_crypto_fish_dat_prod$TL/inv_crypto_fish_dat_prod$MaxSizeTL)*inv_crypto_fish_dat_prod$MaxSizeTL))

#plug back age into VGBF to calculate growth
age <- (1:365) / 365

#set up table for new lengths: 1 column per day, 1 row per individual fish
inv_crypto_fish_vb_len_tab <- matrix (ncol = length (age), nrow = nrow (inv_crypto_fish_dat_prod), dimnames = list (NULL, paste ('Day', 1:365, sep="_")))

#for each individual, calculate new length for that day using VBGF formula (written above)
for (u in 1:nrow (inv_crypto_fish_dat_prod)) {
  
  inv_crypto_fish_vb_len_tab [u, ] <- inv_crypto_fish_dat_prod$MaxSizeTL[u]*(1-exp(-inv_crypto_fish_dat_prod$Kmax[u]*(inv_crypto_fish_dat_prod$EstAge[u]+age))) 
  
}
##convert length to weight using a,b coefs
inv_crypto_fish_vb_wt_tab <- apply (inv_crypto_fish_vb_len_tab, 2, function (x) inv_crypto_fish_dat_prod$LW_a * (x ^ inv_crypto_fish_dat_prod$LW_b))

#create production table (in grams, weight) per day
inv_crypto_fish_biomass_not_rounded_g <- (inv_crypto_fish_dat_prod$LW_a*inv_crypto_fish_dat_prod$TL^inv_crypto_fish_dat_prod$LW_b)
inv_crypto_fish_vb_wt_tab <- cbind(inv_crypto_fish_biomass_not_rounded_g, inv_crypto_fish_vb_wt_tab)
colnames(inv_crypto_fish_vb_wt_tab)[1] <- "Day_0"
inv_crypto_fish_vb_prod_wt_tab <- inv_crypto_fish_vb_wt_tab

for (u in 2:ncol(inv_crypto_fish_vb_prod_wt_tab))
  for (v in 1:nrow(inv_crypto_fish_vb_prod_wt_tab)) {
    inv_crypto_fish_vb_prod_wt_tab [v,u ] <- inv_crypto_fish_vb_wt_tab[v,u]-inv_crypto_fish_vb_wt_tab[v,(u-1)]
  }

inv_crypto_fish_vb_prod_wt_tab2<-inv_crypto_fish_vb_prod_wt_tab[,2:ncol(inv_crypto_fish_vb_prod_wt_tab)]

#incorporate size-dependant mortality for net productivity

inv_crypto_fish_dat_prod$logZyear<- (-0.0066-(0.279*log(inv_crypto_fish_dat_prod$MaxSizeTL))+(0.6543*log(inv_crypto_fish_dat_prod$Kmax))+(0.4634*log(28)))
inv_crypto_fish_dat_prod$Zyear<-exp(inv_crypto_fish_dat_prod$logZyear)

inv_crypto_fish_dat_prod$Zday<-inv_crypto_fish_dat_prod$Zyear/365

#calculate probability of survival
#probability of survival = exp(-zday)
inv_crypto_fish_dat_prod$SurvivalDay<-exp(-inv_crypto_fish_dat_prod$Zday)

#vector of daily survival probabilities for the year
inv_crypto_fish_psurv_tab <- matrix (ncol = 365, nrow = nrow (inv_crypto_fish_dat_prod), dimnames = list (NULL, paste ('Day', 1:365)))
for (u in 1:nrow (inv_crypto_fish_dat_prod)) {
  inv_crypto_fish_psurv_tab [u, ] <- exp(-inv_crypto_fish_dat_prod$Zday[u]) 
}

#simulate mortality per day

inv_crypto_fish_surv_outcome_day <- matrix (ncol = 365, nrow = nrow (inv_crypto_fish_psurv_tab))

for (u in 1:nrow(inv_crypto_fish_psurv_tab))
  for (v in 1:ncol(inv_crypto_fish_psurv_tab)) {
    inv_crypto_fish_surv_outcome_day [u,v ] <- rbern(1,prob= inv_crypto_fish_psurv_tab[u,v])
  }

nrow(subset(inv_crypto_fish_surv_outcome_day,rowSums(inv_crypto_fish_surv_outcome_day)!=365))
nrow(subset(inv_crypto_fish_surv_outcome_day,rowSums(inv_crypto_fish_surv_outcome_day)==365)) 

inv_crypto_fish_surv_outcome_day2<-adply(inv_crypto_fish_surv_outcome_day, 1, zero_row_replace)
inv_crypto_fish_surv_outcome_day2<-dplyr::select(inv_crypto_fish_surv_outcome_day2, -c(X1)) #remove first row, don't want that

nrow(subset(inv_crypto_fish_surv_outcome_day2,rowSums(inv_crypto_fish_surv_outcome_day2)!=365))
nrow(subset(inv_crypto_fish_surv_outcome_day2,rowSums(inv_crypto_fish_surv_outcome_day2)==365))

#multiply survival table*production table to get production estimates
inv_crypto_fish_est_daily_prod_tab <- inv_crypto_fish_surv_outcome_day2*inv_crypto_fish_vb_prod_wt_tab2

#um daily production over the course of a year
inv_crypto_fish_prod_year <- rowSums(inv_crypto_fish_est_daily_prod_tab)

#final conversions and save above simulation
inv_crypto_fish_dat_prod_final <- inv_crypto_fish_dat_prod
inv_crypto_fish_dat_prod_final$prod_year_g <- inv_crypto_fish_prod_year

#convert to kg/ha
inv_crypto_fish_dat_prod_final$prod_year_kg_h <- inv_crypto_fish_dat_prod_final$prod_year_g/inv_crypto_fish_dat_prod_final$Area*10

#for station-level prod analyses
inv_crypto_fish.site.prod.data <- ddply(inv_crypto_fish_dat_prod_final, c("Atoll", "Island", "Site"), summarise,
                  Prod = sum(prod_year_kg_h)) %>% 
  right_join(crypto_site_list) %>% 
  mutate(Prod = ifelse(Prod == 0 | is.na(Prod), 0.001, Prod))

#combine with other data
inv_crypto_fish_chagos_site_prod <- merge(inv_crypto_fish_chagos_div_site, inv_crypto_fish.site.prod.data, by = c("Atoll", "Island", "Site"), all.x = T)

inv_crypto_fish.site.prod.data <- inv_crypto_fish.biomass.data_site %>% 
  left_join(inv_crypto_fish_chagos_site_prod, by = c("Atoll", "Island", "Site", "Biomass"))  %>% 
  right_join(crypto_site_list) %>% 
  mutate(Prod = ifelse(Prod == 0 | is.na(Prod), 0.001, Prod))

#for island-level prod analyses
inv_crypto_fish.island.prod.data <- inv_crypto_fish.site.prod.data %>%
  group_by(Atoll, Island) %>%
  summarise(Prod = mean(Prod, na.rm = T))

#combine with other data
inv_crypto_fish_chagos_island_prod <- merge(inv_crypto_fish_chagos_div_island, inv_crypto_fish.island.prod.data, by = c("Atoll", "Island"), all.x = T)

inv_crypto_fish.island.prod.data <- inv_crypto_fish.biomass.data_island %>% 
  select(-Biomass) %>% 
  left_join(inv_crypto_fish_chagos_island_prod, by = c("Atoll", "Island")) 

```

```{r data-mediators-prod-crypto-island}

crypto_fish.island.prod.df <- crypto_fish.island.prod.data %>% 
  ungroup() %>% 
  mutate(Taxon = "Crypto_fish", Year = 2023) %>% 
  select(Taxon, Atoll, Island, Prod, Year, Biomass)

inv_crypto_fish.island.prod.df <- inv_crypto_fish.island.prod.data %>% 
  ungroup() %>% 
  mutate(Taxon = "Inv_crypto_fish", Year = 2023) %>% 
  select(Taxon, Atoll, Island, Prod, Year, Biomass)

crypto_inv.island.prod.df <- prod_inv_data_island %>% 
  ungroup() %>% 
  mutate(Taxon = "Crypto_inv", Year = 2023) %>% 
  select(Taxon, Atoll, Island, Prod, Year, Biomass)

mediators_productivity_island <- rbind(crypto_fish.island.prod.df, inv_crypto_fish.island.prod.df, crypto_inv.island.prod.df)

mediators_productivity_island_wide <- mediators_productivity_island %>% 
  select(-Year) %>% 
  group_by(Atoll, Island, Taxon) %>%
  pivot_wider(names_from  = Taxon,
    values_from = c(Prod, Biomass),
    names_sep   = "_")

```

```{r data-mediators-prod-crypto-site}

crypto_fish.prod.df <- crypto_fish.site.prod.data %>% 
  ungroup() %>% 
  mutate(Taxon = "Crypto_fish", Year = 2023) %>% 
  select(Taxon, Atoll, Island, Prod, Year, Biomass, Site)

inv_crypto_fish.prod.df <- inv_crypto_fish.site.prod.data %>% 
  ungroup() %>% 
  mutate(Taxon = "Inv_crypto_fish", Year = 2023) %>% 
  select(Taxon, Atoll, Island, Prod, Year, Biomass, Site)

crypto_inv.prod.df <- prod_inv_data_site %>% 
  ungroup() %>% 
  mutate(Taxon = "Crypto_inv", Year = 2023) %>% 
  select(Taxon, Atoll, Island, Prod, Year, Biomass, Site)

mediators_productivity_site <- rbind(crypto_fish.prod.df, inv_crypto_fish.prod.df, crypto_inv.prod.df)

mediators_productivity_site_wide <- mediators_productivity_site %>% 
  select(-Year) %>% 
  group_by(Site, Taxon) %>%
  pivot_wider(names_from  = Taxon,
    values_from = c(Prod, Biomass),
    names_sep   = "_")

```

# Calculate UVC productivity

```{r uvc-data}

# Format data

traits <- read.csv('data/CHA23_UVC_traits.csv')
kmax_list <- read.csv('data/DS2.csv') ##Supplemental file from from Morais and Bellwood 2019 with Kmax data in it

```

```{r prod-all-groups}

# mapping
diet_map <- c(
  inv   = "Invertivore",
  pisc  = "Piscivore",
  det   = "Detritivore",
  cor   = "Corallivore",
  carn  = "Carnivore",
  plank = "Planktivore",
  herb  = "Herbivore",
  omni  = "Omnivore")

uvc_transect_list <- uvc_raw %>%
  distinct(Atoll, Island, Transect, Year) 

# helper: power-of-10 offset from minimum positive value
order_of_magnitude_offset <- function(x) {
  10 ^ floor(log10(min(x[!is.na(x) & x > 0])))
}

build_group <- function(code, diet_label) {
  # calculate productivity per group
  dat <- uvc_raw %>%
    filter(Diet == diet_label) %>%
    filter(!is.na(Length)) 
  
  kmax_28 <- kmax_list[kmax_list$sstmean == 28, ]
  sp_uvc_kmax <- merge(traits, kmax_28, by = c("MaxSizeTL", "Diet", "Position"), all.x = TRUE)
  sp_uvc_kmax_2 <- unique(sp_uvc_kmax)

  dat_k <- merge(dat, sp_uvc_kmax_2, by = c("Species", "Family"), all.x = TRUE)

  dat_k$Length <- ifelse(dat_k$Length > dat_k$MaxSizeTL_Prod, dat_k$MaxSizeTL_Prod, dat_k$Length)
  dat_prod <- dat_k

  dat_prod$EstAge <- (1 / dat_prod$Kmax) * log(
    (dat_prod$MaxSizeTL_Prod) /
      ((1 - dat_prod$Length / dat_prod$MaxSizeTL_Prod) * dat_prod$MaxSizeTL_Prod))

  age <- (1:365) / 365

  vb_len_tab <- matrix(
    ncol = length(age),
    nrow = nrow(dat_prod),
    dimnames = list(NULL, paste("Day", 1:365, sep = "_")))

  for (u in 1:nrow(dat_prod)) {
    vb_len_tab[u, ] <- dat_prod$MaxSizeTL_Prod[u] *
      (1 - exp(-dat_prod$Kmax[u] * (dat_prod$EstAge[u] + age)))
  }

  vb_wt_tab <- apply(vb_len_tab, 2, function(x) dat_prod$a * (x ^ dat_prod$b))

  biomass_not_rounded_g <- (dat_prod$a * dat_prod$Length ^ dat_prod$b)
  vb_wt_tab <- cbind(biomass_not_rounded_g, vb_wt_tab)
  colnames(vb_wt_tab)[1] <- "Day_0"
  vb_prod_wt_tab <- vb_wt_tab

  for (u in 2:ncol(vb_prod_wt_tab)) {
    for (v in 1:nrow(vb_prod_wt_tab)) {
      vb_prod_wt_tab[v, u] <- vb_wt_tab[v, u] - vb_wt_tab[v, (u - 1)]
    }
  }

  vb_prod_wt_tab2 <- vb_prod_wt_tab[, 2:ncol(vb_prod_wt_tab)]

  dat_prod$logZyear <- (-0.0066 - (0.279 * log(dat_prod$MaxSizeTL_Prod)) +
                          (0.6543 * log(dat_prod$Kmax)) + (0.4634 * log(28)))
  dat_prod$Zyear <- exp(dat_prod$logZyear)
  dat_prod$Zday <- dat_prod$Zyear / 365

  psurv_tab <- matrix(ncol = 365, nrow = nrow(dat_prod), dimnames = list(NULL, paste("Day", 1:365)))
  for (u in 1:nrow(dat_prod)) {
    psurv_tab[u, ] <- exp(-dat_prod$Zday[u])
  }

  surv_outcome_day <- matrix(
    rbern(length(psurv_tab), prob = as.vector(psurv_tab)),
    nrow(psurv_tab), ncol(psurv_tab)
  )

  surv_outcome_day2 <- adply(surv_outcome_day, 1, zero_row_replace)
  surv_outcome_day2 <- dplyr::select(surv_outcome_day2, -c(X1))

  est_daily_prod_tab <- surv_outcome_day2 * vb_prod_wt_tab2
  prod_year <- rowSums(est_daily_prod_tab)

  dat_prod_final <- dat_prod
  dat_prod_final$prod_year_g <- prod_year
  dat_prod_final$prod_year_kg_h <- dat_prod_final$prod_year_g / dat_prod_final$Area * 10

  prod_trans <- ddply(dat_prod_final, c("Year", "Atoll", "Island", "Transect"), summarise,
                      total_prod_year = sum(prod_year_kg_h))
  
  # C) Join + per-group offsets
  prod_offset   <- order_of_magnitude_offset(prod_trans$total_prod_year)

  prod_df <- uvc_transect_list %>%
    left_join(prod_trans, by = c("Year", "Atoll", "Island", "Transect")) %>%
    mutate(Diet = diet_label,
           Prod = ifelse(is.na(total_prod_year), prod_offset, total_prod_year + prod_offset))

  list(
    prod = prod_df,
    offsets = c(prod_offset = prod_offset))
}

# Run for all groups
out_list <- lapply(names(diet_map), function(code) build_group(code, diet_map[[code]]))
names(out_list) <- names(diet_map)

# Export objects 
prod_objs    <- setNames(lapply(out_list, `[[`, "prod"),
                         paste0("uvc_", names(out_list), ".prod.data"))

list2env(prod_objs, envir = .GlobalEnv)

```

```{r data-outcomes-prod-uvc}

outcomes_uvc <- bind_rows(uvc_inv.prod.data, 
                      uvc_pisc.prod.data, 
                      uvc_carn.prod.data, 
                      uvc_plank.prod.data, 
                      uvc_omni.prod.data, 
                      uvc_cor.prod.data, 
                      uvc_det.prod.data, 
                      uvc_herb.prod.data) %>%
  select(Prod, Island, Atoll, Year, Transect, Diet)

outcomes_uvc_wide <- outcomes_uvc %>%
  pivot_wider(
    id_cols = c(Island, Atoll, Year, Transect),
    names_from = Diet,
    values_from = Prod,
    names_glue = "{.value}_{Diet}")

outcomes_uvc_wide_island <- outcomes_uvc %>%
  group_by(Island, Atoll, Diet) %>% 
  summarize(Prod = mean(Prod, na.rm = T)) %>% 
  pivot_wider(
    id_cols = c(Island, Atoll),
    names_from = Diet,
    values_from = Prod,
    names_glue = "{.value}_{Diet}")

```

# DAG

```{r dag}

dag <- dagitty("
dag {

seabirds -> coral_symbiont_nutrients
seabirds -> pom_nutrients
seabirds -> turf_nutrients

turf_nutrients -> crypto_inv_productivity
turf_nutrients -> detritus_nutrients
turf_nutrients -> turf_productivity
turf_nutrients -> crypto_fish_productivity
turf_nutrients -> omnivore_productivity

turf_productivity -> herbivore_productivity
turf_productivity -> omnivore_productivity
turf_productivity -> crypto_fish_productivity
turf_productivity -> crypto_inv_productivity

coral_symbiont_nutrients -> coral_growth
coral_symbiont_nutrients -> coral_host_nutrients

coral_host_nutrients -> detritus_nutrients
coral_host_nutrients -> corallivore_detritus_nutrients
coral_host_nutrients -> corallivore_productivity
coral_host_nutrients -> coral_growth

coral_growth -> corallivore_productivity

pom_nutrients -> detritus_nutrients
pom_nutrients -> planktonic_day_nutrients
pom_nutrients -> planktonic_night_nutrients

planktonic_day_nutrients -> planktonic_day_productivity
planktonic_day_nutrients -> planktivore_productivity
planktonic_day_nutrients -> crypto_fish_productivity
planktonic_day_nutrients -> omnivore_productivity

planktonic_night_nutrients -> planktonic_night_productivity
planktonic_night_nutrients -> coral_host_nutrients
planktonic_night_nutrients -> coral_growth
planktonic_night_nutrients -> crypto_inv_productivity
planktonic_night_nutrients -> planktivore_productivity
planktonic_night_nutrients -> omnivore_productivity

planktonic_day_productivity -> planktivore_productivity
planktonic_day_productivity -> omnivore_productivity
planktonic_day_productivity -> crypto_fish_productivity

planktonic_night_productivity -> crypto_inv_productivity
planktonic_night_productivity -> coral_growth
planktonic_night_productivity -> planktivore_productivity

corallivore_detritus_nutrients -> detritus_nutrients
fish_detritus_nutrients -> detritus_nutrients

detritus_nutrients -> detritivore_productivity
detritus_nutrients -> omnivore_productivity
detritus_nutrients -> crypto_fish_productivity
detritus_nutrients -> crypto_inv_productivity

detritus_production -> crypto_fish_productivity
detritus_production -> crypto_inv_productivity
detritus_production -> detritivore_productivity
detritus_production -> omnivore_productivity

crypto_fish_productivity -> carnivore_productivity
crypto_fish_productivity -> piscivore_productivity

crypto_inv_productivity -> carnivore_productivity
crypto_inv_productivity -> invertivore_productivity
crypto_inv_productivity -> omnivore_productivity

inv_crypto_fish_productivity -> crypto_inv_productivity

herbivore_productivity -> detritus_production
planktivore_productivity -> detritus_production
corallivore_productivity -> detritus_production

planktivore_productivity -> piscivore_productivity

turf_productivity[latent]
pom_productivity[latent]
fish_detritus_nutrients[latent]
planktonic_day_productivity[latent]
planktonic_night_productivity[latent]

herbivore_productivity[outcome]
planktivore_productivity[outcome]
detritivore_productivity[outcome]
invertivore_productivity[outcome]
omnivore_productivity[outcome]
piscivore_productivity[outcome]
carnivore_productivity[outcome]
corallivore_productivity[outcome]
seabirds[exposure]


}")

```

# Format data

```{r data-scm}

uvc <- outcomes_uvc %>% 
  left_join(mediators_nutrients_wide) %>% 
  left_join(mediators_productivity_island_wide) %>% 
  left_join(sb_data, by = c("Island", "Atoll")) 

```

# Calculate total effect of seabirds on fish productivity

```{r total-effect}

#pisc total effect 

m_total_pisc <- brm(Prod ~ log(Seabird_Biomass_density_prop) + (1|Atoll/Island) + (1|Year), 
                              control = list(adapt_delta = 0.99, max_treedepth = 15),
  family = Gamma(link = "log"), data = uvc %>% filter(Diet == "Piscivore"))

summary(m_total_pisc)
hypothesis(m_total_pisc, "logSeabird_Biomass_density_prop > 0") #0.98 

#inv total effect

m_total_inv <- brm(Prod ~ log(Seabird_Biomass_density_prop) + (1|Atoll/Island) + (1|Year),
                             control = list(adapt_delta = 0.99, max_treedepth = 15), 
  family = Gamma(link = "log"), data = uvc %>% filter(Diet == "Invertivore"))

summary(m_total_inv)
hypothesis(m_total_inv, "logSeabird_Biomass_density_prop > 0") #0.39

#plank total effect

m_total_plank <- brm(Prod ~ log(Seabird_Biomass_density_prop) + (1|Atoll/Island) + (1|Year),
                               control = list(adapt_delta = 0.9, max_treedepth = 12),
  family = Gamma(link = "log"), data = uvc %>% filter(Diet == "Planktivore"))

summary(m_total_plank)
hypothesis(m_total_plank, "logSeabird_Biomass_density_prop > 0") #0.84 

#carn total effect

m_total_carn <- brm(Prod ~ log(Seabird_Biomass_density_prop) + (1|Atoll/Island) + (1|Year),
                              control = list(adapt_delta = 0.9, max_treedepth = 12),
  family = Gamma(link = "log"), data = uvc %>% filter(Diet == "Carnivore"))

summary(m_total_carn)
hypothesis(m_total_carn, "logSeabird_Biomass_density_prop > 0") #0.92

#cor total effect

m_total_cor <- brm(Prod ~ log(Seabird_Biomass_density_prop) + (1|Atoll/Island) + (1|Year),
                             control = list(adapt_delta = 0.9, max_treedepth = 12),
  family = Gamma(link = "log"), data = uvc %>% filter(Diet == "Corallivore"))

summary(m_total_cor)
hypothesis(m_total_cor, "logSeabird_Biomass_density_prop > 0") #0.81

#omni total effect

m_total_omni <- brm(Prod ~ log(Seabird_Biomass_density_prop) + (1|Atoll/Island) + (1|Year),
                              control = list(adapt_delta = 0.99, max_treedepth = 15),
  family = Gamma(link = "log"), data = uvc %>% filter(Diet == "Omnivore"))

summary(m_total_omni)
hypothesis(m_total_omni, "logSeabird_Biomass_density_prop > 0") #0.59

#det total effect

m_total_det <- brm(Prod ~ log(Seabird_Biomass_density_prop) + (1|Atoll/Island) + (1|Year),
                             control = list(adapt_delta = 0.9, max_treedepth = 12),
  family = Gamma(link = "log"), data = uvc %>% filter(Diet == "Detritivore"))

summary(m_total_det)
hypothesis(m_total_det, "logSeabird_Biomass_density_prop > 0") #0.94

#herb total effect

m_total_herb <- brm(Prod ~ log(Seabird_Biomass_density_prop) + (1|Atoll/Island) + (1|Year),
                              control = list(adapt_delta = 0.9, max_treedepth = 12),
  family = Gamma(link = "log"), data = uvc %>% filter(Diet == "Herbivore"))

summary(m_total_herb)
hypothesis(m_total_herb, "logSeabird_Biomass_density_prop > 0") #0.99

# total

uvc_tot <- uvc %>% 
  group_by(Island, Atoll, Transect, Year) %>% 
  summarize(Prod = sum(Prod)) %>% 
  left_join(sb_data)

m_total_tot <- brm(Prod ~ log(Seabird_Biomass_density_prop) + (1|Atoll/Island) + (1|Year),
                              control = list(adapt_delta = 0.9, max_treedepth = 12),
  family = Gamma(link = "log"), data = uvc_tot)

summary(m_total_tot)
hypothesis(m_total_tot, "logSeabird_Biomass_density_prop > 0") #0.99

# Calculate effect of doubling seabird density

draws_m_total_tot <- spread_draws(m_total_tot, b_logSeabird_Biomass_density_prop)
doubling_effect_m_total_tot <- draws_m_total_tot %>%
  mutate(effect_doubling = exp(b_logSeabird_Biomass_density_prop * log(2)))
median(doubling_effect_m_total_tot$effect_doubling)
hdi(doubling_effect_m_total_tot$effect_doubling, ci = 0.95)
mean(doubling_effect_m_total_tot$effect_doubling > 1)

# pisc 
draws_m_total_pisc <- spread_draws(m_total_pisc, b_logSeabird_Biomass_density_prop)
doubling_effect_m_total_pisc <- draws_m_total_pisc %>%
  mutate(effect_doubling = exp(b_logSeabird_Biomass_density_prop * log(2)))
median(doubling_effect_m_total_pisc$effect_doubling)
hdi(doubling_effect_m_total_pisc$effect_doubling, ci = 0.95)

# herb
draws_m_total_herb <- spread_draws(m_total_herb, b_logSeabird_Biomass_density_prop)
doubling_effect_m_total_herb <- draws_m_total_herb %>%
  mutate(effect_doubling = exp(b_logSeabird_Biomass_density_prop * log(2)))
median(doubling_effect_m_total_herb$effect_doubling)
hdi(doubling_effect_m_total_herb$effect_doubling, ci = 0.95)

# det
draws_m_total_det <- spread_draws(m_total_det, b_logSeabird_Biomass_density_prop)
doubling_effect_m_total_det <- draws_m_total_det %>%
  mutate(effect_doubling = exp(b_logSeabird_Biomass_density_prop * log(2)))
median(doubling_effect_m_total_det$effect_doubling)
hdi(doubling_effect_m_total_det$effect_doubling, ci = 0.95)

# carn
draws_m_total_carn <- spread_draws(m_total_carn, b_logSeabird_Biomass_density_prop)
doubling_effect_m_total_carn <- draws_m_total_carn %>%
  mutate(effect_doubling = exp(b_logSeabird_Biomass_density_prop * log(2)))
median(doubling_effect_m_total_carn$effect_doubling)
hdi(doubling_effect_m_total_carn$effect_doubling, ci = 0.95)
```


```{r plot-fig4a}

# data

pisc.pred <- uvc %>%
  filter(Diet == "Piscivore") %>% 
  data_grid(Seabird_Biomass_density_prop = seq_range(Seabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_total_pisc, re_formula = NA) 

inv.pred <- uvc %>%
  filter(Diet == "Invertivore") %>% 
  data_grid(Seabird_Biomass_density_prop = seq_range(Seabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_total_inv, re_formula = NA) 

plank.pred <- uvc %>% 
  filter(Diet == "Planktivore") %>% 
  data_grid(Seabird_Biomass_density_prop = seq_range(Seabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_total_plank, re_formula = NA) 

carn.pred <- uvc %>%
  filter(Diet == "Carnivore") %>% 
  data_grid(Seabird_Biomass_density_prop = seq_range(Seabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_total_carn, re_formula = NA) 

cor.pred <- uvc %>%
  filter(Diet == "Corallivore") %>% 
  data_grid(Seabird_Biomass_density_prop = seq_range(Seabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_total_cor, re_formula = NA) 

omni.pred <- uvc %>% 
  filter(Diet == "Omnivore") %>% 
  data_grid(Seabird_Biomass_density_prop = seq_range(Seabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_total_omni, re_formula = NA) 

det.pred <- uvc %>% 
  filter(Diet == "Detritivore") %>% 
  data_grid(Seabird_Biomass_density_prop = seq_range(Seabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_total_det, re_formula = NA) 

herb.pred <- uvc %>%
  filter(Diet == "Herbivore") %>% 
  data_grid(Seabird_Biomass_density_prop = seq_range(Seabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_total_herb, re_formula = NA) 

#island-atoll averages

plot.pisc_a <- ggplot(pisc.pred, aes(x = log(Seabird_Biomass_density_prop), y = log(Prod))) + 
  stat_lineribbon(aes(y = log(.epred)), color = "red4", .width = c(0.8, 0.95)) +
  geom_point(data = uvc %>% filter(Diet == "Piscivore") %>% 
               group_by(Atoll, Island) %>% mutate(Prod = mean(Prod)), color = "red4") +
  scale_fill_manual(values = alpha(c("red4", "red1"), 0.2)) +
  xlab(bquote(Log-Seabird~biomass~(kg~ha^-1))) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.y = element_text(colour = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent")) +
  coord_cartesian(clip = "off")

plot.inv_a <- ggplot(inv.pred, aes(x = log(Seabird_Biomass_density_prop), y = log(Prod))) +
  stat_lineribbon(aes(y = log(.epred)), color = "orange4", .width = c(0.8, 0.95)) +
  geom_point(data = uvc %>% filter(Diet == "Invertivore") %>% 
               group_by(Atoll, Island) %>% mutate(Prod = mean(Prod)), color = "orange4") +
  scale_fill_manual(values = alpha(c("orange4", "orange1"), 0.2)) +
  xlab(bquote(Log-Seabird~biomass~(kg~ha^-1))) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.y = element_text(colour = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent")) +
  coord_cartesian(clip = "off")

plot.plank_a <- ggplot(plank.pred, aes(x = log(Seabird_Biomass_density_prop), y = log(Prod))) +
  stat_lineribbon(aes(y = log(.epred)), color = "turquoise4", .width = c(0.8, 0.95)) +
  geom_point(data = uvc %>% filter(Diet == "Planktivore") %>% 
               group_by(Atoll, Island) %>% mutate(Prod = mean(Prod)), color = "turquoise4") +
  scale_fill_manual(values = alpha(c("turquoise4", "turquoise1"), 0.2)) +
  xlab(bquote(Log-Seabird~biomass~(kg~ha^-1))) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.y = element_text(colour = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent")) +
  coord_cartesian(clip = "off")

plot.carn_a <- ggplot(carn.pred, aes(x = log(Seabird_Biomass_density_prop), y = log(Prod))) +
  stat_lineribbon(aes(y = log(.epred)), color = "orangered4", .width = c(0.8, 0.95)) +
  geom_point(data = uvc %>% filter(Diet == "Carnivore") %>% 
               group_by(Atoll, Island) %>% mutate(Prod = mean(Prod)), color = "orangered4") +
  scale_fill_manual(values = alpha(c("orangered4", "orangered1"), 0.2)) +
  scale_y_continuous(breaks = c(-2, 0, 2)) +
  xlab(bquote(Log-Seabird~biomass~(kg~ha^-1))) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.y = element_text(colour = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent")) +
  coord_cartesian(clip = "off") 

plot.cor_a <- ggplot(cor.pred, aes(x = log(Seabird_Biomass_density_prop), y = log(Prod))) +
  stat_lineribbon(aes(y = log(.epred)), color = "darkorchid4", .width = c(0.8, 0.95)) +
  geom_point(data = uvc %>% filter(Diet == "Corallivore") %>% 
               group_by(Atoll, Island) %>% mutate(Prod = mean(Prod)), color = "darkorchid4") +
  scale_fill_manual(values = alpha(c("darkorchid4", "darkorchid1"), 0.2)) +
  xlab(bquote(Log-Seabird~biomass~(kg~ha^-1))) +
  theme(axis.line = element_line(colour = "black"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent")) +
  ylab(bquote("Log-Productivity (kg. " ~ha^-1~")")) +
  coord_cartesian(clip = "off")

plot.omni_a <- ggplot(omni.pred, aes(x = log(Seabird_Biomass_density_prop), y = log(Prod))) +
  stat_lineribbon(aes(y = log(.epred)), color = "violetred4", .width = c(0.8, 0.95)) +
  geom_point(data = uvc %>% filter(Diet == "Omnivore") %>% 
               group_by(Atoll, Island) %>% mutate(Prod = mean(Prod)), color = "violetred4") +
  scale_fill_manual(values = alpha(c("violetred4", "violetred1"), 0.2)) +
  xlab(bquote(Log-Seabird~biomass~(kg~ha^-1))) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.y = element_text(colour = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent")) +
  coord_cartesian(clip = "off")

plot.det_a <- ggplot(det.pred, aes(x = log(Seabird_Biomass_density_prop), y = log(Prod))) +
  stat_lineribbon(aes(y = log(.epred)), color = "slategray4", .width = c(0.8, 0.95)) +
  geom_point(data = uvc %>% filter(Diet == "Detritivore") %>% 
               group_by(Atoll, Island) %>% mutate(Prod = mean(Prod)), color = "slategray4") +
  scale_fill_manual(values = alpha(c("slategray4", "slategray1"), 0.2)) +
  xlab(bquote(Log-Seabird~biomass~(kg~ha^-1))) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.y = element_text(colour = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent")) +
  coord_cartesian(clip = "off")

plot.herb_a <- ggplot(herb.pred, aes(x = log(Seabird_Biomass_density_prop), y = log(Prod))) +
  stat_lineribbon(aes(y = log(.epred)), color = "seagreen4", .width = c(0.8, 0.95)) +
  geom_point(data = uvc %>% filter(Diet == "Herbivore") %>% 
               group_by(Atoll, Island) %>% mutate(Prod = mean(Prod)), color = "seagreen4") +
  scale_fill_manual(values = alpha(c("seagreen4", "seagreen1"), 0.2)) +
  xlab(bquote(Log-Seabird~biomass~(kg~ha^-1))) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.y = element_text(colour = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent")) +
  coord_cartesian(clip = "off")

plot.legend_fig2a <- ggplot(herb.pred, aes(x = log(Seabird_Biomass_density_prop), y = log(Prod))) +
  stat_lineribbon(aes(y = log(.epred))) +   # dummy layer to create legend
  scale_fill_manual(
    values = c("0.8"= alpha("grey80", 0.2), "0.95"=alpha("grey20", 0.2)),
    name = "CI level") 

plot_fig2a <- ggarrange(plot.herb_a + rremove("xlab") + rremove("x.text") + rremove("legend") + rremove("ticks"), 
                        plot.plank_a + rremove("xlab") + rremove("x.text") + rremove("legend") + rremove("ticks"), 
          plot.det_a + rremove("xlab") + rremove("x.text") + rremove("legend") + rremove("ticks"), 
          plot.cor_a + rremove("xlab") + rremove("x.text") + rremove("legend") + rremove("ticks"), 
          plot.omni_a + rremove("xlab") + rremove("x.text") + rremove("legend") + rremove("ticks"), 
          plot.carn_a + rremove("xlab") + rremove("x.text") + rremove("legend") + rremove("ticks"), 
          plot.inv_a + rremove("xlab") + rremove("x.text") + rremove("legend") + rremove("ticks"), 
          plot.pisc_a + rremove("legend") + rremove("ticks"),
          common.legend = T, legend = "none", heights = c(rep(1,7), 1.6),
          ncol = 1, align = "v")
```

```{r plot-fig4b}

plot.herb_b <- spread_draws(m_total_herb, b_logSeabird_Biomass_density_prop) %>%
  ggplot(aes(y = 0, x = b_logSeabird_Biomass_density_prop, fill = after_stat(x > 0))) +
  annotation_custom(img_herb, xmin = 0.1, xmax = 1.5, ymin = 0, ymax = 1.3) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_x_continuous(limits = c(-0.2, 0.4)) +
  scale_y_continuous(breaks = c(0, 0.5, 1)) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.y = element_text(colour = "white"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent")) + 
  theme(plot.margin = margin(t = 5.5, r = 90, b = 5.5, l = 15)) +
  coord_cartesian(clip = "off")

plot.plank_b <- spread_draws(m_total_plank, b_logSeabird_Biomass_density_prop) %>%
  ggplot(aes(y = 0, x = b_logSeabird_Biomass_density_prop, fill = after_stat(x > 0))) + 
  annotation_custom(img_plank, xmin = 0.1, xmax = 1.5, ymin = 0, ymax = 1.3) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_x_continuous(limits = c(-0.2, 0.4)) +
  scale_y_continuous(breaks = c(0, 0.5, 1)) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.y = element_text(colour = "white"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent")) + 
  theme(plot.margin = margin(t = 5.5, r = 90, b = 5.5, l = 15)) +
  coord_cartesian(clip = "off")

plot.det_b <- spread_draws(m_total_det, b_logSeabird_Biomass_density_prop) %>%
  ggplot(aes(y = 0, x = b_logSeabird_Biomass_density_prop, fill = after_stat(x > 0))) + 
  annotation_custom(img_det, xmin = 0.1, xmax = 1.5, ymin = 0, ymax = 1.3) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_x_continuous(limits = c(-0.2, 0.4)) +
  scale_y_continuous(breaks = c(0, 0.5, 1)) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.y = element_text(colour = "white"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent")) + 
  theme(plot.margin = margin(t = 5.5, r = 90, b = 5.5, l = 15)) +
  coord_cartesian(clip = "off")

plot.cor_b <- spread_draws(m_total_cor, b_logSeabird_Biomass_density_prop) %>%
  ggplot(aes(y = 0, x = b_logSeabird_Biomass_density_prop, fill = after_stat(x > 0))) + 
  annotation_custom(img_cor, xmin = 0.1, xmax = 1.5, ymin = 0, ymax = 1.3) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_x_continuous(limits = c(-0.2, 0.4)) +
  scale_y_continuous(breaks = c(0, 0.5, 1)) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.y = element_text(colour = "white"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent")) + 
  theme(plot.margin = margin(t = 5.5, r = 90, b = 5.5, l = 15)) +
  coord_cartesian(clip = "off")

plot.omni_b <- spread_draws(m_total_omni, b_logSeabird_Biomass_density_prop) %>%
  ggplot(aes(y = 0, x = b_logSeabird_Biomass_density_prop, fill = after_stat(x > 0))) +
  annotation_custom(img_omni, xmin = 0.1, xmax = 1.5, ymin = 0, ymax = 1.3) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_x_continuous(limits = c(-0.2, 0.4)) +
  scale_y_continuous(breaks = c(0, 0.5, 1)) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.y = element_text(colour = "white"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent")) + 
  theme(plot.margin = margin(t = 5.5, r = 90, b = 5.5, l = 15)) +
  coord_cartesian(clip = "off")

plot.carn_b <- spread_draws(m_total_carn, b_logSeabird_Biomass_density_prop) %>%
  ggplot(aes(y = 0, x = b_logSeabird_Biomass_density_prop, fill = after_stat(x > 0))) + 
  annotation_custom(img_carn, xmin = 0.1, xmax = 1.5, ymin = 0, ymax = 1.3) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_x_continuous(limits = c(-0.2, 0.4)) +
  scale_y_continuous(breaks = c(0, 0.5, 1)) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.y = element_text(colour = "white"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent")) + 
  theme(plot.margin = margin(t = 5.5, r = 90, b = 5.5, l = 15)) +
  coord_cartesian(clip = "off")

plot.inv_b <- spread_draws(m_total_inv, b_logSeabird_Biomass_density_prop) %>%
  ggplot(aes(y = 0, x = b_logSeabird_Biomass_density_prop, fill = after_stat(x > 0))) + 
  annotation_custom(img_inv, xmin = 0.1, xmax = 1.5, ymin = 0, ymax = 1.3) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_x_continuous(limits = c(-0.2, 0.4)) +
  scale_y_continuous(breaks = c(0, 0.5, 1)) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.y = element_text(colour = "white"),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent")) + 
  theme(plot.margin = margin(t = 5.5, r = 90, b = 5.5, l = 15)) +
  coord_cartesian(clip = "off")

plot.pisc_b <- spread_draws(m_total_pisc, b_logSeabird_Biomass_density_prop) %>%
  ggplot(aes(y = 0, x = b_logSeabird_Biomass_density_prop, fill = after_stat(x > 0))) +
  annotation_custom(img_pisc, xmin = 0.15, xmax = 1.5, ymin = 0, ymax = 1.3) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af"), labels = c("≤ 0", "> 0")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_x_continuous(limits = c(-0.2, 0.4)) +
  scale_y_continuous(breaks = c(0, 0.5, 1)) +
  guides(fill = guide_legend(title = "Effect direction")) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.y = element_text(colour = "white"),
        axis.title.x = element_text(vjust = -2),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent")) +
  labs(x = "Posterior estimate") +
  theme(plot.margin = margin(t = 5.5, r = 90, b = 15, l = 15)) +
  coord_cartesian(clip = "off")

legend_fig2a <- get_legend(plot.legend_fig2a) 

legend_fig2b <- get_legend(plot.pisc_b) 

blank_legend <- get_legend(plot.legend_fig2a)  +
    theme(legend.position = "right",
      plot.margin = margin(0, 0, 0, l = 20),
      legend.box.margin = margin(0, 0, 0, l = 20))

legend_fig2 <- ggarrange(blank_legend, legend_fig2a, legend_fig2b, blank_legend, align = "hv", nrow = 4) 
  
plot_fig2b <- ggarrange(plot.herb_b + rremove("xlab") + rremove("x.text") + rremove("legend") + rremove("ticks"), 
                        plot.plank_b + rremove("xlab") + rremove("x.text") + rremove("legend") + rremove("ticks"), 
                        plot.det_b + rremove("xlab") + rremove("x.text") + rremove("legend") + rremove("ticks"), 
                        plot.cor_b + rremove("xlab") + rremove("x.text") + rremove("legend") + rremove("ticks"), 
                        plot.omni_b + rremove("xlab") + rremove("x.text") + rremove("legend") + rremove("ticks"), 
                        plot.carn_b + rremove("xlab") + rremove("x.text") + rremove("legend") + rremove("ticks"), 
                        plot.inv_b + rremove("xlab") + rremove("x.text") + rremove("legend") + rremove("ticks"), 
                        plot.pisc_b + rremove("ticks"),
                        legend = "none", heights = c(rep(1,7), 1.5),
                        ncol = 1)  

plot_fig4 <- ggarrange(legend_fig2, plot_fig2a, plot_fig2b, legend = "none", ncol = 3, align = "hv", labels = c("", "a", "b"), widths = c(0.6, 0.9, 1.4))

plot_fig4

ggsave("figures/main/Fig4.png", plot_fig4, width = 6, height = 8, units = "in", dpi = 600)
  
```

##I. Basal resources

# I. A. Nutrients

```{r direct effect-basal-resources-n15}

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "turf_nutrients",
  effect = "direct")

# turf

dat_turf_n15 <- mediators_nutrients %>% filter(Taxon == "Turf") %>% left_join(sb_data, by = c("Island", "Atoll", "Seabird_Biomass_density_prop")) %>% 
  mutate(logSeabird_Biomass_density_prop = log(Seabird_Biomass_density_prop))

m_turf_n15 <- brm(N15 ~ logSeabird_Biomass_density_prop + (1|Atoll/Island), data = dat_turf_n15, control = list(adapt_delta = 0.99, max_treedepth = 15))

summary(m_turf_n15)
hypothesis(m_turf_n15, "logSeabird_Biomass_density_prop > 0") #0.91

# plankton

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "pom_nutrients",
  effect = "direct")

#{}

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "pom_nutrients",
  effect = "total")

#{}

dat_pom_n15 <- mediators_nutrients %>% filter(Taxon == "POM") %>% left_join(sb_data, by = c("Island", "Atoll", "Seabird_Biomass_density_prop")) %>% 
  mutate(logSeabird_Biomass_density_prop = log(Seabird_Biomass_density_prop))

m_pom_n15 <- brm(N15 ~ logSeabird_Biomass_density_prop + (1|Atoll/Island), data = dat_pom_n15, control = list(adapt_delta = 0.99, max_treedepth = 15))

summary(m_pom_n15)
hypothesis(m_pom_n15, "logSeabird_Biomass_density_prop > 0") #0.92

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "planktonic_night_nutrients",
  effect = "direct")

#{ pom_nutrients }

dat_plank_night_n15 <- mediators_nutrients %>% filter(Taxon == "Plank_night") %>% left_join(sb_data, by = c("Island", "Atoll", "Seabird_Biomass_density_prop")) %>% 
  mutate(logSeabird_Biomass_density_prop = log(Seabird_Biomass_density_prop)) %>% 
  left_join(mediators_nutrients_wide, by = c("Island", "Atoll"))

prior_n15 <- c(
  prior(normal(0, 0.5), class = "b"),
  prior(exponential(1), class = "sigma"),
  prior(exponential(2), class = "sd"))

m_plank_night_n15_direct <- brm(N15 ~ logSeabird_Biomass_density_prop + N15_POM + (1|Atoll/Island), data = dat_plank_night_n15, prior = prior_n15, control = list(adapt_delta = 0.99, max_treedepth = 15))

summary(m_plank_night_n15_direct)
hypothesis(m_plank_night_n15_direct, "logSeabird_Biomass_density_prop > 0") #0.7
hypothesis(m_plank_night_n15_direct, "N15_POM > 0") #0.53

m_plank_night_n15_total <- brm(N15 ~ logSeabird_Biomass_density_prop + (1|Atoll/Island), data = dat_plank_night_n15, control = list(adapt_delta = 0.99, max_treedepth = 15))

summary(m_plank_night_n15_total)
hypothesis(m_plank_night_n15_total, "logSeabird_Biomass_density_prop > 0") #0.85

dat_plankton_n15 <- mediators_nutrients %>% filter(Taxon == "Plankton") %>% left_join(sb_data, by = c("Island", "Atoll", "Seabird_Biomass_density_prop")) %>% 
  mutate(logSeabird_Biomass_density_prop = log(Seabird_Biomass_density_prop)) %>% 
  left_join(mediators_nutrients_wide, by = c("Island", "Atoll"))

m_plankton_n15_total <- brm(N15 ~ logSeabird_Biomass_density_prop + (1|Atoll/Island), data = dat_plankton_n15, control = list(adapt_delta = 0.99, max_treedepth = 15))

summary(m_plankton_n15_total)
hypothesis(m_plankton_n15_total, "logSeabird_Biomass_density_prop > 0") #0.7

m_plankton_n15_direct <- brm(N15 ~ logSeabird_Biomass_density_prop + N15_POM + (1|Atoll/Island), data = dat_plankton_n15, control = list(adapt_delta = 0.99, max_treedepth = 15))

summary(m_plankton_n15_direct)
hypothesis(m_plankton_n15_direct, "logSeabird_Biomass_density_prop > 0") #0.7
hypothesis(m_plankton_n15_direct, "N15_POM > 0") #0.62

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "coral_symbiont_nutrients",
  effect = "total")

#{} total = direct

dat_symbiont_n15 <- mediators_nutrients %>% filter(Taxon == "Symbiont") %>% left_join(sb_data, by = c("Island", "Atoll", "Seabird_Biomass_density_prop")) %>% 
  mutate(logSeabird_Biomass_density_prop = log(Seabird_Biomass_density_prop))

m_symbiont_n15 <- brm(N15 ~ logSeabird_Biomass_density_prop + (1|Atoll/Island), data = dat_symbiont_n15, control = list(adapt_delta = 0.99, max_treedepth = 15))

summary(m_symbiont_n15)
hypothesis(m_symbiont_n15, "logSeabird_Biomass_density_prop > 0") #0.93

dat_host_n15 <- mediators_nutrients %>% filter(Taxon == "Coral") %>% left_join(sb_data, by = c("Island", "Atoll", "Seabird_Biomass_density_prop")) %>% 
  mutate(logSeabird_Biomass_density_prop = log(Seabird_Biomass_density_prop))

m_host_n15 <- brm(N15 ~ logSeabird_Biomass_density_prop + (1|Atoll/Island), data = dat_host_n15, control = list(adapt_delta = 0.99, max_treedepth = 15))

summary(m_host_n15)
hypothesis(m_host_n15, "logSeabird_Biomass_density_prop > 0") #0.91

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "detritus_nutrients",
  effect = "direct")

# { coral_host_nutrients, pom_nutrients, turf_nutrients }

dat_det_n15 <- mediators_nutrients %>% filter(Taxon == "Detritus") %>% left_join(sb_data, by = c("Island", "Atoll", "Seabird_Biomass_density_prop")) %>% 
  mutate(logSeabird_Biomass_density_prop = log(Seabird_Biomass_density_prop))

m_det_n15_total <- brm(N15 ~ logSeabird_Biomass_density_prop + (1|Atoll/Island), data = dat_det_n15, control = list(adapt_delta = 0.99, max_treedepth = 15))

summary(m_det_n15_total)
hypothesis(m_det_n15_total, "logSeabird_Biomass_density_prop > 0") #0.99

dat_det_n15_direct <- mediators_nutrients %>% filter(Taxon == "Detritus") %>% left_join(sb_data, by =c("Island", "Atoll", "Seabird_Biomass_density_prop")) %>% 
  mutate(logSeabird_Biomass_density_prop = log(Seabird_Biomass_density_prop)) %>% 
  left_join(mediators_nutrients_wide, by = c("Island", "Atoll"))

m_det_n15_direct <- brm(N15 ~ logSeabird_Biomass_density_prop + N15_Turf + N15_POM + N15_Coral + (1|Atoll/Island), prior = prior_n15, data = dat_det_n15_direct, control = list(adapt_delta = 0.99, max_treedepth = 15))

summary(m_det_n15_direct)
hypothesis(m_det_n15_direct, "logSeabird_Biomass_density_prop > 0") #0.57
hypothesis(m_det_n15_direct, "N15_Turf > 0") #0.5
hypothesis(m_det_n15_direct, "N15_POM > 0") #0.5
hypothesis(m_det_n15_direct, "N15_Coral > 0") #0.57

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "corallivore_detritus_nutrients",
  effect = "total")

dat_chaetrif_det_n15 <- mediators_nutrients %>% filter(Taxon == "Chaetrif_detritus") %>% left_join(sb_data, by = c("Island", "Atoll", "Seabird_Biomass_density_prop")) %>% 
  mutate(logSeabird_Biomass_density_prop = log(Seabird_Biomass_density_prop)) %>% 
  left_join(mediators_nutrients_wide, by = c("Island", "Atoll"))

m_chaetrif_det_n15_total <- brm(N15 ~ logSeabird_Biomass_density_prop + (1|Atoll/Island), data = dat_chaetrif_det_n15, control = list(adapt_delta = 0.99, max_treedepth = 15))

summary(m_chaetrif_det_n15_total)
hypothesis(m_chaetrif_det_n15_total, "logSeabird_Biomass_density_prop > 0") #0.89


```

```{r plot-figs3}

#turf

turf_n15.pred <- dat_turf_n15 %>%
  data_grid(logSeabird_Biomass_density_prop = seq_range(logSeabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_turf_n15, re_formula = NA) 

plot.turf_n15 <- ggplot(turf_n15.pred, aes(x = logSeabird_Biomass_density_prop, y = N15)) + 
  annotation_custom(img_turf_n15, xmin = -1.6, xmax = 0.7, ymin = 6.7, ymax = 8) +
  stat_lineribbon(aes(y = .epred), color = "seagreen4") +
  geom_point(data = dat_turf_n15 %>% group_by(Atoll, Island, logSeabird_Biomass_density_prop) %>% summarize(N15 = mean(N15, na.rm = T)), color = "seagreen4") +
  scale_fill_manual(values = alpha(c("seagreen3", "seagreen", "seagreen4"), 0.2)) +
  ylab(expression(Turf~delta^15*N~"\U2030")) +
  xlab(bquote(Log-Seabird~biomass~(kg~ha^-1))) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 9),
        panel.grid = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent"),
        legend.position = "none") +
  coord_cartesian(clip = "off")

#symbiont

symbiont_n15.pred <- dat_symbiont_n15 %>%
  data_grid(logSeabird_Biomass_density_prop = seq_range(logSeabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_symbiont_n15, re_formula = NA) 

plot.symbiont_n15 <- ggplot(symbiont_n15.pred, aes(x = logSeabird_Biomass_density_prop, y = N15)) + 
  annotation_custom(img_symbiont_n15, xmin = -3.2, xmax = 0.4, ymin = 7.6, ymax = 8.9) +
  stat_lineribbon(aes(y = .epred), color = "darkorchid4") +
  geom_point(data = dat_symbiont_n15 %>% group_by(Atoll, Island, logSeabird_Biomass_density_prop) %>% summarize(N15 = mean(N15, na.rm = T)), color = "darkorchid4") +
  scale_fill_manual(values = alpha(c("darkorchid4", "darkorchid3", "darkorchid1"), 0.2)) +
  xlab(bquote(Log-Seabird~biomass~(kg~ha^-1))) +
  ylab(expression("Coral "~symbiont~delta^15*N~"\U2030")) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 9),
        panel.grid = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent"),
        legend.position = "none") +
  coord_cartesian(clip = "off")

#effect line

pom_n15.pred <- dat_pom_n15 %>%
  data_grid(logSeabird_Biomass_density_prop = seq_range(logSeabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_pom_n15, re_formula = NA) 

plot.pom_n15 <- ggplot(pom_n15.pred, aes(x = logSeabird_Biomass_density_prop, y = N15)) + 
  annotation_custom(img_pom_n15, xmin = -3, xmax = -0.3, ymin = 7.9, ymax = 9.3) +
  stat_lineribbon(aes(y = .epred), color = "turquoise4") +
  geom_point(data = dat_pom_n15 %>% group_by(Atoll, Island, logSeabird_Biomass_density_prop) %>% summarize(N15 = mean(N15, na.rm = T)), color = "turquoise4") +
  scale_fill_manual(values = alpha(c("turquoise4", "turquoise3", "turquoise1"), 0.2)) +
  xlab(bquote(Log-Seabird~biomass~(kg~ha^-1))) +
  ylab(expression("Particulate Organic "~Matter~delta^15*N~"\U2030")) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 9),
        panel.grid = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent"),
        legend.position = "none") +
  coord_cartesian(clip = "off")

#effect line

det_n15.pred <- dat_det_n15 %>%
  data_grid(logSeabird_Biomass_density_prop = seq_range(logSeabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_det_n15_total, re_formula = NA) 

plot.det_n15 <- ggplot(det_n15.pred, aes(x = logSeabird_Biomass_density_prop, y = N15)) + 
  annotation_custom(img_det_n15, xmin = -2, xmax = 0.6, ymin = 6.9, ymax = 8.1) +
  stat_lineribbon(aes(y = .epred), color = "slategray4") +
  geom_point(data = dat_det_n15 %>% group_by(Atoll, Island, logSeabird_Biomass_density_prop) %>% summarize(N15 = mean(N15, na.rm = T)), color = "slategray4") +
  scale_fill_manual(values = alpha(c("slategray3", "slategray", "slategray4"), 0.3)) +
  xlab(bquote(Log-Seabird~biomass~(kg~ha^-1))) +
  ylab(expression(Detritus~delta^15*N~"\U2030")) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 9),
        panel.grid = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent"),
        legend.position = "none") +
  coord_cartesian(clip = "off")

plot_fig1_a.a <- ggarrange(plot.turf_n15, plot.pom_n15, plot.symbiont_n15, plot.det_n15, nrow = 1)
  
plot_fig1_a <- annotate_figure(plot_fig1_a.a, bottom = text_grob(bquote(Seabird~biomass~(kg~ha^-1)), size = 11))

plot_fig1_a

# supp figure

# plank_night

turf_n15.pred <- dat_turf_n15 %>%
  data_grid(logSeabird_Biomass_density_prop = seq_range(logSeabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_turf_n15, re_formula = NA) 

plot.turf_n15 <- ggplot(turf_n15.pred, aes(x = logSeabird_Biomass_density_prop, y = N15)) + 
  annotation_custom(img_turf_n15, xmin = -1.6, xmax = 0.7, ymin = 6.7, ymax = 8) +
  stat_lineribbon(aes(y = .epred), color = "seagreen4") +
  geom_point(data = dat_turf_n15 %>% group_by(Atoll, Island, logSeabird_Biomass_density_prop) %>% summarize(N15 = mean(N15, na.rm = T)), color = "seagreen4") +
  scale_fill_manual(values = alpha(c("seagreen3", "seagreen", "seagreen4"), 0.2)) +
  ylab(expression(Turf~delta^15*N~"\U2030")) +
  xlab(bquote(Log-Seabird~biomass~(kg~ha^-1))) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 9),
        panel.grid = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent"),
        legend.position = "none") +
  coord_cartesian(clip = "off")

#host

host_n15.pred <- dat_host_n15 %>%
  data_grid(logSeabird_Biomass_density_prop = seq_range(logSeabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_host_n15, re_formula = NA) 

plot.host_n15 <- ggplot(host_n15.pred, aes(x = logSeabird_Biomass_density_prop, y = N15)) + 
  stat_lineribbon(aes(y = .epred), color = "darkorchid4") +
  geom_point(data = dat_host_n15 %>% group_by(Atoll, Island, logSeabird_Biomass_density_prop) %>% summarize(N15 = mean(N15, na.rm = T)), color = "darkorchid4") +
  scale_fill_manual(values = alpha(c("darkorchid4", "darkorchid3", "darkorchid1"), 0.2)) +
  xlab(bquote(Log-Seabird~biomass~(kg~ha^-1))) +
  ylab(expression("Coral "~host~delta^15*N~"\U2030")) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 9),
        panel.grid = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent"),
        legend.position = "none") +
  coord_cartesian(clip = "off")

#effect line

plank_night_n15.pred <- dat_plank_night_n15 %>%
  data_grid(logSeabird_Biomass_density_prop = seq_range(logSeabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_plank_night_n15_total, re_formula = NA) 

plot.plank_night_n15 <- ggplot(plank_night_n15.pred, aes(x = logSeabird_Biomass_density_prop, y = N15)) + 
  stat_lineribbon(aes(y = .epred), color = "turquoise4") +
  geom_point(data = dat_plank_night_n15 %>% group_by(Atoll, Island, logSeabird_Biomass_density_prop) %>% summarize(N15 = mean(N15, na.rm = T)), color = "turquoise4") +
  scale_fill_manual(values = alpha(c("turquoise4", "turquoise3", "turquoise1"), 0.2)) +
  xlab(bquote(Log-Seabird~biomass~(kg~ha^-1))) +
  ylab(expression("Night "~Zooplankton~delta^15*N~"\U2030")) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 9),
        panel.grid = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent"),
        legend.position = "none") +
  coord_cartesian(clip = "off")

plankton_n15.pred <- dat_plankton_n15 %>%
  data_grid(logSeabird_Biomass_density_prop = seq_range(logSeabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_plankton_n15_total, re_formula = NA) 

plot.plankton_n15 <- ggplot(plankton_n15.pred, aes(x = logSeabird_Biomass_density_prop, y = N15)) + 
  stat_lineribbon(aes(y = .epred), color = "turquoise4") +
  geom_point(data = dat_plankton_n15 %>% group_by(Atoll, Island, logSeabird_Biomass_density_prop) %>% summarize(N15 = mean(N15, na.rm = T)), color = "turquoise4") +
  scale_fill_manual(values = alpha(c("turquoise4", "turquoise3", "turquoise1"), 0.2)) +
  xlab(bquote(Log-Seabird~biomass~(kg~ha^-1))) +
  ylab(expression("Day "~Zooplankton~delta^15*N~"\U2030")) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 9),
        panel.grid = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent"),
        legend.position = "none") +
  coord_cartesian(clip = "off")

#corallivore feces

chaetrif_det_n15.pred <- dat_chaetrif_det_n15 %>%
  data_grid(logSeabird_Biomass_density_prop = seq_range(logSeabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_chaetrif_det_n15_total, re_formula = NA) 

plot.chaetrif_det_n15 <- ggplot(chaetrif_det_n15.pred, aes(x = logSeabird_Biomass_density_prop, y = N15)) + 
  stat_lineribbon(aes(y = .epred), color = "slategray4") +
  geom_point(data = dat_chaetrif_det_n15 %>% group_by(Atoll, Island, logSeabird_Biomass_density_prop) %>% summarize(N15 = mean(N15, na.rm = T)), color = "slategray4") +
  scale_fill_manual(values = alpha(c("slategray3", "slategray", "slategray4"), 0.3)) +
  xlab(bquote(Log-Seabird~biomass~(kg~ha^-1))) +
  ylab(expression("Corallivore "~detritus~delta^15*N~"\U2030")) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 9),
        panel.grid = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent"),
        legend.position = "none") +
  coord_cartesian(clip = "off")

plot_fig_supp_a <- ggarrange(plot.plank_night_n15, plot.plankton_n15, plot.host_n15, plot.chaetrif_det_n15, nrow = 1)
  
plot_fig_supp_a.a <- annotate_figure(plot_fig_supp_a, bottom = text_grob(bquote(Seabird~biomass~(kg~ha^-1)), size = 11))

#legend

plot.legend.supp <- ggplot(plank_night_n15.pred,
  aes(x = logSeabird_Biomass_density_prop, y = .epred)) +
  stat_lineribbon() +
  scale_fill_manual(
     values = c("0.5" = alpha("grey80", 0.2), "0.8"= alpha("grey50", 0.2), "0.95"=alpha("grey20", 0.2)),
     name = "CI level") +
  theme(legend.position = "right")

legend_supp <- cowplot::get_legend(plot.legend.supp)

plot_fig_supp <- ggarrange(legend_supp, plot_fig_supp_a.a, nrow = 1, widths = c(0.15, 1)) 

#ggsave("figures/supp/FigS3.png", plot_fig_supp, width = 8, height = 2.5, units = "in", dpi = 600)

```

# I. B. Production

```{r direct effect-crypto-inv-site}

# 1. Crypto_inv_productivity

dat_crypto_inv_prod_site <- prod_inv_data_site %>% 
  group_by(Site, Atoll, Island) %>% 
  summarize(Prod = mean(Prod, na.rm = T)) %>% #individual prod already accounts for Area
  left_join(mediators_nutrients_wide, by = c("Atoll", "Island")) %>% 
  left_join(mediators_productivity_site_wide, by = c("Site", "Atoll", "Island")) %>% 
  left_join(sb_data, by = c("Atoll", "Island")) %>% 
  left_join(outcomes_uvc_wide_island, by = c("Atoll", "Island")) %>% 
  left_join(egestion_dat_island, by = c("Atoll", "Island"))

prior_crypto_inv_prod_site <- c(
  prior(normal(0, 1), class = "b"),
  prior(exponential(1), class = "sd"),
  prior(exponential(1), class = "shape"))

# turf -> crypto_inv_productivity

# total

adjustmentSets(dag,
  exposure = "turf_nutrients", 
  outcome = "crypto_inv_productivity",
  effect = "total")

#can't do direct
#{ coral_symbiont_nutrients, pom_nutrients }
#{ seabirds }

m_crypto_inv_prod_turf_plank_total_site <- brm(Prod ~ N15_Turf + N15_POM + N15_Symbiont + (1|Atoll/Island), data = dat_crypto_inv_prod_site, prior = prior_crypto_inv_prod_site, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_crypto_inv_prod_turf_plank_total_site)
hypothesis(m_crypto_inv_prod_turf_plank_total_site, "N15_Turf > 0") #0.49
hypothesis(m_crypto_inv_prod_turf_plank_total_site, "N15_POM > 0") #0.49
hypothesis(m_crypto_inv_prod_turf_plank_total_site, "N15_Symbiont > 0") #0.37

# plank_night

adjustmentSets(dag,
  exposure = "planktonic_night_nutrients", 
  outcome = "crypto_inv_productivity",
  effect = "total")

#{ pom_nutrients }

m_crypto_inv_prod_plank_total_site <- brm(Prod ~ N15_Plank_night + N15_POM + (1|Atoll/Island), data = dat_crypto_inv_prod_site, prior = prior_crypto_inv_prod_site, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_crypto_inv_prod_plank_total_site)
hypothesis(m_crypto_inv_prod_plank_total_site, "N15_POM > 0") #0.37
hypothesis(m_crypto_inv_prod_plank_total_site, "N15_Plank_night > 0") #0.43

adjustmentSets(dag,
  exposure = "detritus_nutrients",
  outcome = "crypto_inv_productivity",
  effect = "direct")

#{ coral_host_nutrients, pom_nutrients, turf_nutrients }

m_crypto_inv_prod_det_n15_site <- brm(Prod ~ N15_Detritus + N15_Coral + N15_POM + N15_Turf + (1|Atoll/Island), data = dat_crypto_inv_prod_site, prior = prior_crypto_inv_prod_site, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_crypto_inv_prod_det_n15_site)
hypothesis(m_crypto_inv_prod_det_n15_site, "N15_Turf > 0") #0.49
hypothesis(m_crypto_inv_prod_det_n15_site, "N15_POM > 0") #0.49
hypothesis(m_crypto_inv_prod_det_n15_site, "N15_Coral > 0") #0.39
hypothesis(m_crypto_inv_prod_det_n15_site, "N15_Detritus > 0") #0.49

adjustmentSets(dag,
  exposure = "detritus_production", 
  outcome = "crypto_inv_productivity",
  effect = "total")

# total = direct =
#{ herbivore_productivity, planktivore_productivity, corallivore_productivity }

m_crypto_inv_prod_det_prod_site <- brm(Prod ~ log(Wc) + log(Prod_Herbivore) + log(Prod_Planktivore) + log(Prod_Corallivore) + (1|Atoll/Island), data = dat_crypto_inv_prod_site, prior = prior_crypto_inv_prod_site, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_crypto_inv_prod_det_prod_site)
hypothesis(m_crypto_inv_prod_det_prod_site, "logWc > 0") #0.33

# 3. seabirds -> crypto_inv_productivity

adjustmentSets(dag,
  exposure = "seabirds",
  outcome = "crypto_inv_productivity",
  effect = "total")

# {}

m_crypto_inv_prod_sb_total_site <- brm(Prod ~ log(Seabird_Biomass_density_prop) + (1|Atoll/Island), data = dat_crypto_inv_prod_site, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_crypto_inv_prod_sb_total_site)
hypothesis(m_crypto_inv_prod_sb_total_site, "logSeabird_Biomass_density_prop > 0") #0.25

adjustmentSets(dag,
  exposure = "seabirds",
  outcome = "crypto_inv_productivity",
  effect = "direct")

#{ pom_nutrients, turf_nutrients, coral_symbiont_nutrients }

m_crypto_inv_prod_sb_direct_site <- brm(Prod ~ log(Seabird_Biomass_density_prop) + N15_POM + N15_Turf + N15_Symbiont + (1|Atoll/Island), data = dat_crypto_inv_prod_site, prior = prior_crypto_inv_prod_site, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_crypto_inv_prod_sb_direct_site)
hypothesis(m_crypto_inv_prod_sb_direct_site, "logSeabird_Biomass_density_prop > 0") #0.45
hypothesis(m_crypto_inv_prod_sb_direct_site, "N15_POM > 0") #0.5
hypothesis(m_crypto_inv_prod_sb_direct_site, "N15_Turf > 0") #0.51
hypothesis(m_crypto_inv_prod_sb_direct_site, "N15_Symbiont > 0") #0.47

adjustmentSets(dag,
  exposure = "inv_crypto_fish_productivity",
  outcome = "crypto_inv_productivity",
  effect = "direct")

# total = direct =  {}

m_crypto_inv_prod_inv_crypto_fish_site <- brm(Prod ~ log(Prod_Inv_crypto_fish) + (1|Atoll/Island), data = dat_crypto_inv_prod_site, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_crypto_inv_prod_inv_crypto_fish_site)
hypothesis(m_crypto_inv_prod_inv_crypto_fish_site, "logProd_Inv_crypto_fish > 0") #0.06

```


```{r direct effect-crypto-fish-site}

# 1. Crypto fish productivity

# data

dat_crypto_fish_prod_site <- crypto_fish.site.prod.data %>% 
  left_join(mediators_nutrients_wide, by = c("Atoll", "Island")) %>% 
  left_join(mediators_productivity_site_wide, by = c("Site", "Atoll", "Island")) %>% 
  left_join(outcomes_uvc_wide_island, by = c("Atoll", "Island")) %>% 
  left_join(egestion_dat_island, by = c("Atoll", "Island"))

prior_crypto_fish_prod_site <- c(
  prior(normal(0, 1), class = "b"),
  prior(exponential(1), class = "sd"),
  prior(exponential(1), class = "shape"))


adjustmentSets(dag,
  exposure = "turf_nutrients",
  outcome = "crypto_fish_productivity",
  effect = "total")

#total 

#{ coral_symbiont_nutrients, pom_nutrients }
#{ seabirds }

m_crypto_fish_prod_n15_total_site <- brm(Prod ~ N15_Symbiont + N15_POM + N15_Turf + (1|Atoll/Island), data = dat_crypto_fish_prod_site, prior = prior_crypto_fish_prod_site, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_crypto_fish_prod_n15_total_site)
hypothesis(m_crypto_fish_prod_n15_total_site, "N15_Symbiont > 0") #0.49
hypothesis(m_crypto_fish_prod_n15_total_site, "N15_Turf > 0") #0.49
hypothesis(m_crypto_fish_prod_n15_total_site, "N15_POM > 0") #0.5

adjustmentSets(dag,
  exposure = "detritus_nutrients",
  outcome = "crypto_fish_productivity",
  effect = "direct")

#{ coral_host_nutrients, pom_nutrients, turf_nutrients }

m_crypto_fish_prod_det_n15_site <- brm(Prod ~ N15_Detritus + N15_Coral + N15_POM + N15_Turf + (1|Atoll/Island), data = dat_crypto_fish_prod_site, prior = prior_crypto_fish_prod_site, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

hypothesis(m_crypto_fish_prod_det_n15_site, "N15_Detritus > 0") #0.5

adjustmentSets(dag,
  exposure = "detritus_production",
  outcome = "crypto_fish_productivity",
  effect = "direct")

#{ corallivore_productivity,herbivore_productivity, planktivore_productivity }

m_crypto_fish_prod_det_prod_site <- brm(Prod ~ log(Wc) + log(Prod_Planktivore) + log(Prod_Herbivore) + log(Prod_Corallivore) + (1|Atoll/Island), data = dat_crypto_fish_prod_site, prior = prior_crypto_fish_prod_site, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_crypto_fish_prod_det_prod_site)
hypothesis(m_crypto_fish_prod_det_prod_site, "logWc > 0") #0.68

adjustmentSets(dag,
  exposure = "turf_nutrients",
  outcome = "crypto_fish_productivity",
  effect = "direct")

# can't do (no turf prod data)

# 3. seabirds -> crypto_fish_productivity

adjustmentSets(dag,
  exposure = "seabirds",
  outcome = "crypto_fish_productivity",
  effect = "total")

# {}

m_crypto_fish_prod_sb_total_site <- brm(Prod ~ log(Seabird_Biomass_density_prop) + (1|Atoll/Island), data = dat_crypto_fish_prod_site, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_crypto_fish_prod_sb_total_site)
hypothesis(m_crypto_fish_prod_sb_total_site, "logSeabird_Biomass_density_prop > 0") #0.96

# stats

draws_m_crypto_fish_prod_sb_total_site <- spread_draws(m_crypto_fish_prod_sb_total_site, b_logSeabird_Biomass_density_prop)

doubling_effect_m_crypto_fish_prod_sb_total_site <- draws_m_crypto_fish_prod_sb_total_site %>%
  mutate(effect_doubling = exp(b_logSeabird_Biomass_density_prop * log(2)))

median(doubling_effect_m_crypto_fish_prod_sb_total_site$effect_doubling)

hdi(doubling_effect_m_crypto_fish_prod_sb_total_site$effect_doubling, ci = 0.95)

mean(doubling_effect_m_crypto_fish_prod_sb_total_site$effect_doubling > 1)

adjustmentSets(dag,
  exposure = "seabirds",
  outcome = "crypto_fish_productivity",
  effect = "direct")

#{ coral_symbiont_nutrients, pom_nutrients, turf_nutrients }

m_crypto_fish_prod_sb_direct_site <- brm(Prod ~ log(Seabird_Biomass_density_prop) + N15_Turf + N15_POM + N15_Symbiont + (1|Atoll/Island), prior = prior_crypto_fish_prod_site, data = dat_crypto_fish_prod_site, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_crypto_fish_prod_sb_direct_site)
hypothesis(m_crypto_fish_prod_sb_direct_site, "logSeabird_Biomass_density_prop > 0") #0.48
hypothesis(m_crypto_fish_prod_sb_direct_site, "N15_POM > 0") #0.51
hypothesis(m_crypto_fish_prod_sb_direct_site, "N15_Turf > 0") #0.5
hypothesis(m_crypto_fish_prod_sb_direct_site, "N15_Symbiont > 0") #0.5

```

```{r direct effect-detritus}

wc_dat <- egestion_dat %>% 
  left_join(mediators_nutrients_wide, by = c("Atoll", "Island"))

prior_wc <- c(
  prior(normal(0, 1), class = "b"),
  prior(exponential(1), class = "sd"),
  prior(exponential(1), class = "shape"))

# total

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "detritus_production",
  effect = "total")

# {}

m_Wc_total <- brm(Wc ~ log(Seabird_Biomass_density_prop) + (1|Atoll/Island) + (1|Year), prior = prior_wc, data = wc_dat, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12)) 

summary(m_Wc_total)
hypothesis(m_Wc_total, "logSeabird_Biomass_density_prop > 0") #1

draws_m_Wc_total <- spread_draws(m_Wc_total, b_logSeabird_Biomass_density_prop)

doubling_effect_m_Wc_total <- draws_m_Wc_total %>%
  mutate(effect_doubling = exp(b_logSeabird_Biomass_density_prop * log(2)))

median(doubling_effect_m_Wc_total$effect_doubling)

hdi(doubling_effect_m_Wc_total$effect_doubling, ci = 0.95)

mean(doubling_effect_m_Wc_total$effect_doubling > 1)

#direct

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "detritus_production",
  effect = "direct")

#no planktivore or herbivore productivity:
#{ coral_symbiont_nutrients, pom_nutrients, turf_nutrients }

m_Wc_direct <- brm(Wc ~ log(Seabird_Biomass_density_prop) + N15_Symbiont + N15_POM + N15_Turf + (1|Atoll/Island) + (1|Year), prior = prior_wc, data = wc_dat, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12)) 

summary(m_Wc_direct)
hypothesis(m_Wc_direct, "N15_POM > 0") #0.51
hypothesis(m_Wc_direct, "N15_Turf > 0") #0.5
hypothesis(m_Wc_direct, "N15_Symbiont > 0") #0.52
hypothesis(m_Wc_direct, "logSeabird_Biomass_density_prop > 0") #0.51

# effect mediated by those


```

```{r direct effect-coral-growth}

#Coral performance/growth (production)

# data

coral_growth_dat <- read.csv("data/Acropora_SIA_Growth.csv") %>% 
  select(Atoll, Island, Host_N15, Symbiont_N15, diff_SA_year) %>% 
  rename(Growth = diff_SA_year) %>% 
  left_join(sb_data, by = c("Atoll", "Island")) %>% 
  left_join(mediators_nutrients_wide, by = c("Atoll", "Island"))

# coral symbiont nutrients -> coral growth

adjustmentSets(dag,
  exposure = "coral_symbiont_nutrients", 
  outcome = "coral_growth",
  effect = "total")

# total
#{ planktonic_night_nutrients }
#{ pom_nutrients }
#{ seabirds }

m_growth_symbiont_total <- brm(Growth ~ Symbiont_N15 + N15_Plank_night + (1|Atoll/Island), data = coral_growth_dat, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_growth_symbiont_total)
hypothesis(m_growth_symbiont_total, "Symbiont_N15 > 0") #0.83
hypothesis(m_growth_symbiont_total, "N15_Plank_night > 0") #0.65

# direct

adjustmentSets(dag,
  exposure = "coral_symbiont_nutrients", 
  outcome = "coral_growth",
  effect = "direct")

# {coral_host_nutrients, planktonic_night_nutrients}

m_growth_symbiont_direct <- brm(Growth ~ Symbiont_N15 + Host_N15 + N15_Plank_night + (1|Atoll/Island), data = coral_growth_dat, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_growth_symbiont_direct)
hypothesis(m_growth_symbiont_direct, "Symbiont_N15 > 0") #0.35
hypothesis(m_growth_symbiont_direct, "Host_N15 > 0") #0.78
hypothesis(m_growth_symbiont_direct, "N15_Plank_night > 0") #0.6

# coral_host_nutrients -> coral_growth

adjustmentSets(dag,
  exposure = "coral_host_nutrients", 
  outcome = "coral_growth",
  effect = "direct")

# see above

# night_plankton -> coral growth

adjustmentSets(dag,
  exposure = "planktonic_night_nutrients", 
  outcome = "coral_growth",
  effect = "direct")

# can't do direct 

#total = { coral_symbiont_nutrients }
#{ seabirds }
#{ pom_nutrients }

# seabirds -> coral growth

# total

m_growth_sb_total <- brm(Growth ~ log(Seabird_Biomass_density_prop) + (1|Atoll/Island), data = coral_growth_dat, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_growth_sb_total)
hypothesis(m_growth_sb_total, "logSeabird_Biomass_density_prop > 0") #0.67

# direct

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "coral_growth",
  effect = "direct")

# { coral_symbiont_nutrients, planktonic_night_nutrients }

m_growth_sb_direct <- brm(Growth ~ log(Seabird_Biomass_density_prop) + Symbiont_N15 + N15_Plank_night + (1|Atoll/Island), data = coral_growth_dat, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_growth_sb_direct)
hypothesis(m_growth_sb_direct, "logSeabird_Biomass_density_prop > 0") #0.35
hypothesis(m_growth_sb_direct, "Symbiont_N15 > 0") #0.76
hypothesis(m_growth_sb_direct, "N15_Plank_night > 0") #0.7
```

```{r plot-basal-production}

coral_growth.pred <- coral_growth_dat %>%
  data_grid(Seabird_Biomass_density_prop = seq_range(Seabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_growth_sb_total, re_formula = NA) 

plot.coral_growth <- ggplot(coral_growth.pred, aes(x = log(Seabird_Biomass_density_prop), y = log(Growth))) + 
  annotation_custom(img_coral_prod, xmin = -1.7, xmax = 1.5, ymin = 6.4, ymax = 9.6) +
  stat_lineribbon(aes(y = log(.epred)), color = "darkorchid4") +
  geom_point(data = coral_growth_dat, color = "darkorchid4") +
  scale_fill_manual(values = alpha(c("darkorchid4", "darkorchid3", "darkorchid1"), 0.2)) +
  ylab("Log-Coral growth (cm² y⁻¹)") +
  ylab(expression(Log-Coral~growth~(cm^2~yr^-1))) +
  theme(axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 9, lineheight = 1),
        panel.grid = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent"),
        legend.position = "none") +
  coord_cartesian(clip = "off", ylim = c(2, 9))

wc.pred <- wc_dat %>%
  data_grid(Seabird_Biomass_density_prop = seq_range(Seabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_Wc_total, re_formula = NA) 

plot.wc <- ggplot(wc.pred, aes(x = log(Seabird_Biomass_density_prop), y = log(Wc))) + 
  annotation_custom(img_det_prod, xmin = -3.2, xmax = 2, ymin = -3, ymax = -1) +
  stat_lineribbon(aes(y = log(.epred)), color = "slategray4") +
  geom_point(data = wc_dat %>% group_by(Atoll, Island) %>% mutate(Wc = mean(Wc, na.rm = T)), color = "slategray4") +
  scale_fill_manual(values = alpha(c("slategray3", "slategray", "slategray4"), 0.2)) +
  xlab(bquote(Log-Seabird~biomass~(kg~ha^-1))) +
  ylab("Log-Detritus production\n(mg C m⁻² day⁻¹)") +
  theme(axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 9, lineheight = 0.8),
        panel.grid = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent"),
        legend.position = "none") +
  coord_cartesian(clip = "off")

crypto_inv.pred <- dat_crypto_inv_prod_site %>%
  data_grid(Seabird_Biomass_density_prop = seq_range(Seabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_crypto_inv_prod_sb_total_site, re_formula = NA) 

plot.crypto_inv <- ggplot(crypto_inv.pred, aes(x = log(Seabird_Biomass_density_prop), y = log(Prod))) +
  annotation_custom(img_inv_prod, xmin = 2.2, xmax = 8, ymin = 3, ymax = 4.2) +
  stat_lineribbon(aes(y = log(.epred)), color = "orange4") +
  geom_point(data = dat_crypto_inv_prod_site, color = "orange4") +
  scale_fill_manual(values = alpha(c("orange4", "orange3", "orange1"), 0.2)) +
  xlab(bquote(Log-Seabird~biomass~(kg~ha^-1))) +
  ylab("Log-Cryptic invertebrate\nproduction (kg ha⁻¹ y⁻¹)") +
  theme(axis.line = element_line(colour = "black"),
        axis.title.y = element_text(size = 9, lineheight = 0.8),
        axis.title.x = element_blank(),
        panel.grid = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent"),
        legend.position = "none") +
  coord_cartesian(clip = "off", ylim = c(0, 4))

crypto_fish.pred <- dat_crypto_fish_prod_site %>%
  data_grid(Seabird_Biomass_density_prop = seq_range(dat_crypto_fish_prod_site$Seabird_Biomass_density_prop, n = 100)) %>%  
  add_epred_draws(m_crypto_fish_prod_sb_total_site, re_formula = NA) 

plot.crypto_fish <- ggplot(crypto_fish.pred, aes(x = log(Seabird_Biomass_density_prop), y = log(Prod))) + 
  annotation_custom(img_fish_prod, xmin = -1.9, xmax = 1.7, ymin = 3.8, ymax = 6.3) +
  stat_lineribbon(aes(y = log(.epred)), color = "red4") +
  geom_point(data = dat_crypto_fish_prod_site, color = "red4") +
  scale_fill_manual(values = alpha(c("red4", "red3", "red1"), 0.2)) +
  xlab(bquote(Log-Seabird~biomass~(kg~ha^-1))) +
  ylab("Log-Cryptobenthic fish\nproduction (kg ha⁻¹ y⁻¹)") +
  theme(axis.line = element_line(colour = "black"),
        axis.title.y = element_text(size = 9, lineheight = 0.8),
        axis.title.x = element_blank(),
        panel.grid = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent"),
        legend.position = "none") +
  coord_cartesian(clip = "off")

plot.legend <- ggplot(crypto_fish.pred, aes(x = log(Seabird_Biomass_density_prop), y = log(Prod))) +
  stat_lineribbon(aes(y = log(.epred))) +   # dummy layer to create legend
  scale_fill_manual(
    values = c("0.5" = alpha("grey80", 0.2), "0.8"= alpha("grey50", 0.2), "0.95"=alpha("grey20", 0.2)),
    name = "CI level") 

legend <- get_legend(plot.legend)

plot_fig1_b.a <- ggarrange(plot.crypto_fish, plot.crypto_inv, plot.coral_growth, plot.wc, nrow = 1)
  
plot_fig1_b <- annotate_figure(plot_fig1_b.a, bottom = text_grob(bquote(Seabird~biomass~(kg~ha^-1)), size = 11))


plot_fig1.noleg <- ggarrange(plot_fig1_a, plot_fig1_b, nrow = 2, labels = c("a", "b"))

plot_fig1 <- ggarrange(legend, plot_fig1.noleg, nrow = 1, widths = c(0.15, 1)) 

#ggsave("figures/main/Fig1.png", plot_fig1, width = 8, height = 5, units = "in", dpi = 600)


```

##II. Herbivores

```{r direct effect-herbivore}

# data

uvc_herb_prod_direct <- uvc %>% 
  filter(Diet == "Herbivore") 

# already established effect of seabirds on turf above. Now effect of turf N15 on herb productivity

adjustmentSets(dag,
  exposure = "turf_nutrients", 
  outcome = "herbivore_productivity",
  effect = "total")

m_herb_prod_turf <- brm(Prod ~ N15_Turf + (1|Atoll/Island) + (1|Year), data = uvc_herb_prod_direct, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_herb_prod_turf)
hypothesis(m_herb_prod_turf, "N15_Turf > 0") #0.63

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "herbivore_productivity",
  effect = "direct")

#{ turf_nutrients }

m_herb_prod_direct <- brm(Prod ~ log(Seabird_Biomass_density_prop) + N15_Turf + (1|Atoll/Island) + (1|Year), data = uvc_herb_prod_direct, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_herb_prod_direct)
hypothesis(m_herb_prod_direct, "logSeabird_Biomass_density_prop > 0") #0.96
hypothesis(m_herb_prod_direct, "N15_Turf > 0") #0.14 #turf productivity

```

##III. Planktivores

```{r direct effect-plank}

# pom_nutrients -> planktonic_day_nutrients

adjustmentSets(dag,
  exposure = "pom_nutrients", 
  outcome = "planktonic_day_nutrients",
  effect = "direct")

# total = direct = {}

# data

plank_day_dat <- mediators_nutrients %>% filter(Taxon == "Plankton") %>% 
  left_join(mediators_nutrients_wide, by = c("Atoll", "Island"))

uvc_plank_prod_direct <- uvc %>% 
  filter(Diet == "Planktivore") 

m_plank_day_pom <- brm(N15 ~ N15_POM + (1|Atoll/Island), data = plank_day_dat, control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_plank_day_pom)
hypothesis(m_plank_day_pom, "N15_POM > 0") #0.8

# pom_nutrients -> planktonic_night_nutrients

adjustmentSets(dag,
  exposure = "pom_nutrients", 
  outcome = "planktonic_night_nutrients",
  effect = "direct")

# total = direct = {}

plank_night_dat <- mediators_nutrients %>% filter(Taxon == "Plank_night") %>% 
  left_join(mediators_nutrients_wide, by = c("Atoll", "Island"))

m_plank_night_pom <- brm(N15 ~ N15_POM + (1|Atoll/Island), data = plank_night_dat, control = list(adapt_delta = 0.999, max_treedepth = 12))

summary(m_plank_night_pom)
hypothesis(m_plank_night_pom, "N15_POM > 0") #0.62 #makes sense

# because of collinearity, cannot do what follows

# plank_day_nutrients -> planktivore_productivity

adjustmentSets(dag,
  exposure = "planktonic_day_nutrients", 
  outcome = "planktivore_productivity",
  effect = "total")

# { pom_nutrients }


adjustmentSets(dag,
  exposure = "planktonic_day_nutrients", 
  outcome = "planktivore_productivity",
  effect = "direct")

# Cannot do because cannot block planktonic productivity (latent)

m_plank_prod_plank_day_total <- brm(Prod ~ N15_Plankton + N15_POM + (1|Atoll/Island) + (1|Year), data = uvc_plank_prod_direct, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_plank_prod_plank_day_total)
hypothesis(m_plank_prod_plank_day_total, "N15_Plankton > 0") #0.33
hypothesis(m_plank_prod_plank_day_total, "N15_POM > 0") #0.82

m_plank_prod_plank_day_total_b <- brm(Prod ~ N15_Plankton + N15_Plank_night + (1|Atoll/Island) + (1|Year), data = uvc_plank_prod_direct, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_plank_prod_plank_day_total_b)
hypothesis(m_plank_prod_plank_day_total_b, "N15_Plankton > 0") #0.82
hypothesis(m_plank_prod_plank_day_total_b, "N15_Plank_night > 0") #0.11

# plank_night_nutrients -> planktivore_productivity

adjustmentSets(dag,
  exposure = "planktonic_night_nutrients", 
  outcome = "planktivore_productivity",
  effect = "total")

# can't do direct

adjustmentSets(dag,
  exposure = "planktonic_night_nutrients", 
  outcome = "planktivore_productivity",
  effect = "direct")

#can't estimate

# now look at seabirds

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "planktivore_productivity",
  effect = "direct")

#{ pom_nutrients }

m_plank_prod_direct <- brm(Prod ~ log(Seabird_Biomass_density_prop) + N15_POM + (1|Atoll/Island) + (1|Year), data = uvc_plank_prod_direct, family = Gamma(link = "log"))

summary(m_plank_prod_direct)
hypothesis(m_plank_prod_direct, "logSeabird_Biomass_density_prop > 0") #0.33
hypothesis(m_plank_prod_direct, "N15_POM > 0") #0.72

m_plank_prod_direct_b <- brm(Prod ~ log(Seabird_Biomass_density_prop) + N15_Plankton + N15_Plank_night + (1|Atoll/Island) + (1|Year), data = uvc_plank_prod_direct, family = Gamma(link = "log"))

summary(m_plank_prod_direct_b)
hypothesis(m_plank_prod_direct_b, "logSeabird_Biomass_density_prop > 0") #0.43
hypothesis(m_plank_prod_direct_b, "N15_Plankton > 0") #0.77
hypothesis(m_plank_prod_direct_b, "N15_Plank_night > 0") #0.17

exp(fixef(m_plank_prod_direct))

```

##IV. Detritivores

```{r direct-effect-detritivore}

# 1. baseline formation of the detrital pool

# turf_nutrients -> detritus_nutrients

adjustmentSets(dag,
  exposure = "turf_nutrients", 
  outcome = "detritus_nutrients",
  effect = "direct")

#{ coral_host_nutrients, pom_nutrients } # and the reverse is true so 2 birds 1 stone
#{ seabirds }

det_n15_dat <- mediators_nutrients %>% filter(Taxon == "Detritus") %>% 
  left_join(mediators_nutrients_wide, by = c("Island", "Atoll"))

prior_det <- c(
  prior(normal(0, 1), class = "b"),
  prior(exponential(1), class = "sigma"),
  prior(exponential(2), class = "sd"))
  
m_det_n15_turf_direct <- brm(N15 ~ N15_Turf + N15_POM + N15_Coral + (1|Atoll/Island), data = det_n15_dat, prior = prior_det, control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_det_n15_turf_direct)
hypothesis(m_det_n15_turf_direct, "N15_Turf > 0") #0.52
hypothesis(m_det_n15_turf_direct, "N15_POM > 0") #0.52
hypothesis(m_det_n15_turf_direct, "N15_Coral > 0") #0.6

#detritus appears to carry both benthic and pelagic isotopic input

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "detritus_nutrients",
  effect = "direct")

#{ coral_host_nutrients, pom_nutrients, turf_nutrients }
#{ coral_symbiont_nutrients, pom_nutrients, turf_nutrients }

m_det_n15_turf_sb_direct <- brm(N15 ~ N15_Turf + N15_POM + N15_Coral + log(Seabird_Biomass_density_prop) + (1|Atoll/Island), data = det_n15_dat, prior = prior_det, control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_det_n15_turf_sb_direct)
hypothesis(m_det_n15_turf_sb_direct, "N15_Turf > 0") #0.52
hypothesis(m_det_n15_turf_sb_direct, "N15_POM > 0") #0.53
hypothesis(m_det_n15_turf_sb_direct, "N15_Coral > 0") #0.54
hypothesis(m_det_n15_turf_sb_direct, "logSeabird_Biomass_density_prop > 0") #0.57

#detritus δ15N increases with turf δ15N, but also tracks seabird influence -> seabirds enrich the detrital pool through more than one source pathway

# coral_host_nutrients -> detritus_nutrients

adjustmentSets(dag,
  exposure = "coral_host_nutrients", 
  outcome = "detritus_nutrients",
  effect = "direct")

#{ corallivore_detritus_nutrients, pom_nutrients, turf_nutrients }
#{ corallivore_detritus_nutrients, pom_nutrients, seabirds }
#{ corallivore_detritus_nutrients, planktonic_night_nutrients, seabirds }

priors_det_n15 <- c(
  prior(normal(0, 1), class = "b"),
  prior(exponential(1), class = "sigma"),
  prior(exponential(2), class = "sd")
)

m_det_n15_coral_direct <- brm(N15 ~ N15_Turf + N15_Chaetrif_detritus + N15_POM + N15_Coral + (1|Atoll/Island), prior = priors_det_n15, data = det_n15_dat, control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_det_n15_coral_direct)
hypothesis(m_det_n15_coral_direct, "N15_Coral > 0") #0.6
hypothesis(m_det_n15_coral_direct, "N15_Turf > 0") #0.51
hypothesis(m_det_n15_coral_direct, "N15_Chaetrif_detritus > 0") #0.52
hypothesis(m_det_n15_coral_direct, "N15_POM > 0") #0.53

# corallivore detritus nutrients

adjustmentSets(dag,
  exposure = "corallivore_detritus_nutrients", 
  outcome = "detritus_nutrients",
  effect = "total")

adjustmentSets(dag,
  exposure = "corallivore_detritus_nutrients", 
  outcome = "detritus_nutrients",
  effect = "direct")

# total = direct 
# { coral_host_nutrients }

m_det_n15_cor_det_direct <- brm(N15 ~ N15_Chaetrif_detritus + N15_Coral + (1|Atoll/Island), data = det_n15_dat, control = list(adapt_delta = 0.99, max_treedepth = 15))

summary(m_det_n15_cor_det_direct)
hypothesis(m_det_n15_cor_det_direct, "N15_Coral > 0") #0.19
hypothesis(m_det_n15_cor_det_direct, "N15_Chaetrif_detritus > 0") #0.85

# side test

# coral host -> chaetrif detritus

cor_det_n15_dat <- mediators_nutrients %>% filter(Taxon == "Chaetrif_detritus") %>% 
  left_join(mediators_nutrients_wide, by = c("Island", "Atoll"))

adjustmentSets(dag,
  exposure = "coral_host_nutrients", 
  outcome = "corallivore_detritus_nutrients",
  effect = "direct")

# total = direct =  {}

m_cor_det_n15 <- brm(N15 ~ N15_Coral + (1|Atoll/Island), data = cor_det_n15_dat, control = list(adapt_delta = 0.99, max_treedepth = 15))

summary(m_cor_det_n15)
hypothesis(m_cor_det_n15, "N15_Coral > 0") #0.97

# seabirds -> chaetrif nutrients

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "corallivore_detritus_nutrients",
  effect = "total")

# { }

m_cor_det_sb_total <- brm(N15 ~ log(Seabird_Biomass_density_prop) + (1|Atoll/Island), data = cor_det_n15_dat, control = list(adapt_delta = 0.99, max_treedepth = 15))

hypothesis(m_cor_det_sb_total, "logSeabird_Biomass_density_prop > 0") #0.88

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "corallivore_detritus_nutrients",
  effect = "direct")

# { coral_host_nutrients }

m_cor_det_sb_direct <- brm(N15 ~ log(Seabird_Biomass_density_prop) + N15_Coral + (1|Atoll/Island), data = cor_det_n15_dat, control = list(adapt_delta = 0.99, max_treedepth = 15))

hypothesis(m_cor_det_sb_direct, "logSeabird_Biomass_density_prop > 0") #0.76
hypothesis(m_cor_det_sb_direct, "N15_Coral > 0") #0.89

# 2. detrital pathway into downstream consumers

#Wc -> detritivore_productivity

uvc_det_prod_direct <- uvc %>% 
  filter(Diet == "Detritivore") %>%
  left_join(wc_dat %>% group_by(Island, Atoll, Transect, Year, Seabird_Biomass_density_prop) %>% 
              summarize(Wc = mean(Wc, na.rm = T)), 
            by = c("Island", "Atoll", "Transect", "Seabird_Biomass_density_prop", "Year"))

adjustmentSets(dag,
  exposure = "detritus_production", 
  outcome = "detritivore_productivity",
  effect = "direct")

#total = dirct = { detritus_nutrients }

m_det_prod_wc <- brm(Prod ~ log(Wc) + N15_Detritus + (1|Atoll/Island) + (1|Year), data = uvc_det_prod_direct, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_det_prod_wc)
hypothesis(m_det_prod_wc, "logWc > 0") #0.99
hypothesis(m_det_prod_wc, "N15_Detritus > 0") #0.98

# direct effect of seabirds on productivity

adjustmentSets(dag,
  exposure = "seabirds",
  outcome = "detritivore_productivity",
  effect = "direct")

#{ detritus_nutrients, detritus_production }

cor(log(wc_dat$Seabird_Biomass_density_prop),
  log(wc_dat$Wc),
  use = "complete.obs") #0.06

cor(log(uvc_det_prod_direct$Wc),
    log(uvc_det_prod_direct$Prod),
  use = "complete.obs") #0.28

cor(log(uvc_det_prod_direct$Seabird_Biomass_density_prop),
  log(uvc_det_prod_direct$Prod),
  use="complete.obs") #-0.03

cor(mediators_nutrients_wide[,c("N15_POM","N15_Turf","N15_Symbiont")],
    use="complete.obs") # all 1 so explains weak indiv coefficients

m_det_prod_direct <- brm(Prod ~ log(Seabird_Biomass_density_prop) + log(Wc) + N15_Detritus + (1|Atoll/Island) + (1|Year), data = uvc_det_prod_direct, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 15))

summary(m_det_prod_direct)
hypothesis(m_det_prod_direct, "logWc > 0") #0.98
hypothesis(m_det_prod_direct, "N15_Detritus > 0") #0.79
hypothesis(m_det_prod_direct, "logSeabird_Biomass_density_prop > 0") #0.55

```

##V: Corallivores

```{r direct effect-coral}

# 1. formation of coral isotope pathway

# data

host_symbiont_dat <- read.csv("data/CHA18_paired_host_symbiont.csv") %>% 
  filter(Host_sample_ID != "") %>% 
  left_join(mediators_nutrients_wide %>% select(N15_POM, N15_Plank_night, Island, Atoll), by = c("Island", "Atoll")) %>% 
  left_join(sb_data, by = c("Island", "Atoll"))

prior_coral <- c(
  prior(normal(0, 1), class = "b"),
  prior(exponential(1), class = "sigma"),
  prior(exponential(2), class = "sd"))


# 1.a. coral symbionts

# seabirds -> coral symbionts

# already done - see above

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "coral_symbiont_nutrients",
  effect = "direct")

# {}

# coral symbionts -> coral host

# total

m_host_n15_symbiont_total <- brm(Host_N15 ~ Symbiont_N15 + (1|Atoll/Island) + (1|Year), data = host_symbiont_dat, control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_host_n15_symbiont_total)
hypothesis(m_host_n15_symbiont_total, "Symbiont_N15 > 0") #1

# direct

adjustmentSets(dag,
  exposure = "coral_symbiont_nutrients", 
  outcome = "coral_host_nutrients",
  effect = "total")

#{ seabirds }


m_host_n15_direct <- brm(Host_N15 ~ log(Seabird_Biomass_density_prop) + Symbiont_N15 + (1|Atoll/Island) + (1|Year), data = host_symbiont_dat, control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_host_n15_direct)
hypothesis(m_host_n15_direct, "Symbiont_N15 > 0") #1
hypothesis(m_host_n15_direct, "logSeabird_Biomass_density_prop > 0") #0.94

# seabirds -> coral host = direct uptake of dissolved nitrogen

#total

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "coral_host_nutrients",
  effect = "total")

m_host_n15_sb_total <- brm(Host_N15 ~ log(Seabird_Biomass_density_prop) + (1|Atoll/Island) + (1|Year), data = host_symbiont_dat, control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_host_n15_sb_total)
hypothesis(m_host_n15_sb_total, "logSeabird_Biomass_density_prop > 0") #0.92

#direct

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "coral_host_nutrients",
  effect = "direct")

#{ coral_symbiont_nutrients, pom_nutrients }
#{ coral_symbiont_nutrients, planktonic_night_nutrients }

m_host_n15_sb_direct <- brm(Host_N15 ~ log(Seabird_Biomass_density_prop) + N15_POM + Symbiont_N15 + (1|Atoll/Island) + (1|Year), prior = prior_coral, data = host_symbiont_dat, control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_host_n15_sb_direct)
hypothesis(m_host_n15_sb_direct, "logSeabird_Biomass_density_prop > 0") #0.92
hypothesis(m_host_n15_sb_direct, "N15_POM > 0") #0.6
hypothesis(m_host_n15_sb_direct, "Symbiont_N15 > 0") #0.94

m_host_n15_sb_direct_b <- brm(Host_N15 ~ log(Seabird_Biomass_density_prop) + N15_Plank_night + Symbiont_N15 + (1|Atoll/Island) + (1|Year), prior = prior_coral, data = host_symbiont_dat, control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_host_n15_sb_direct_b)
hypothesis(m_host_n15_sb_direct_b, "logSeabird_Biomass_density_prop > 0") #0.71
hypothesis(m_host_n15_sb_direct_b, "N15_Plank_night > 0") #0.46
hypothesis(m_host_n15_sb_direct_b, "Symbiont_N15 > 0") #0.99

# so it really is through symbiont-mediated transfer and not heterotrophic feeding

# planktonic_night_nutrients -> coral host nutrients

# total = direct

adjustmentSets(dag,
  exposure = "planktonic_night_nutrients", 
  outcome = "coral_host_nutrients",
  effect = "direct")

prior_host <- c(
  prior(normal(0, 1), class = "b"),
  prior(exponential(1), class = "sigma"),
  prior(exponential(2), class = "sd"))

#{ coral_symbiont_nutrients }
#{ seabirds }
#{ pom_nutrients }

m_host_n15_plank_night_direct <- brm(Host_N15 ~ N15_POM + N15_Plank_night + (1|Atoll/Island) + (1|Year), data = host_symbiont_dat, prior = prior_host, control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_host_n15_plank_night_direct)
hypothesis(m_host_n15_plank_night_direct, "N15_Plank_night > 0") #0.81

#heterotrophic feeding on night plankton



# 2. Coral performance/growth (production)

# coral symbiont nutrients -> coral growth
# see m_growth_symbiont_direct and m_growth_symbiont_total

# night plankton -> coral growth

adjustmentSets(dag,
  exposure = "planktonic_night_nutrients", 
  outcome = "coral_growth",
  effect = "total")

# { coral_symbiont_nutrients }
#{ seabirds }
#{ pom_nutrients }

adjustmentSets(dag,
  exposure = "planktonic_night_nutrients", 
  outcome = "coral_growth",
  effect = "direct")

#can't do

# seabirds -> coral growth

# Already calculated

# total

summary(m_growth_sb_total)
hypothesis(m_growth_sb_total, "logSeabird_Biomass_density_prop > 0") #0.68

# direct

summary(m_growth_sb_direct)
hypothesis(m_growth_sb_direct, "logSeabird_Biomass_density_prop > 0") #0.34
hypothesis(m_growth_sb_direct, "Symbiont_N15 > 0") #0.79
hypothesis(m_growth_sb_direct, "N15_Plank_night > 0") #0.72


# 3. Coral-to-corallivore transfer

# data

uvc_cor_prod <- uvc %>% 
  filter(Diet == "Corallivore") %>%
  left_join(coral_growth_dat %>% group_by(Island, Atoll, Seabird_Biomass_density_prop) %>% 
              summarize(Growth = mean(Growth, na.rm = T)), 
             by = c("Island", "Atoll", "Seabird_Biomass_density_prop"))

# coral_host_nutrients -> corallivore_productivity

# total

adjustmentSets(dag,
  exposure = "coral_host_nutrients", 
  outcome = "corallivore_productivity",
  effect = "total")

#{ coral_symbiont_nutrients, planktonic_night_nutrients }

m_cor_prod_host_total <- brm(Prod ~ N15_Coral + N15_Plank_night + N15_Symbiont + (1|Atoll/Island) + (1|Year), data = uvc_cor_prod, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_cor_prod_host_total)
hypothesis(m_cor_prod_host_total, "N15_Coral > 0") #0.76

# direct

adjustmentSets(dag,
  exposure = "coral_host_nutrients", 
  outcome = "corallivore_productivity",
  effect = "direct")

#{ coral_growth }
#{ coral_symbiont_nutrients }

m_cor_prod_host_direct <- brm(Prod ~ N15_Coral + log(Growth) + (1|Atoll/Island) + (1|Year), data = uvc_cor_prod, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_cor_prod_host_direct)
hypothesis(m_cor_prod_host_direct, "N15_Coral > 0") #0.82
hypothesis(m_cor_prod_host_direct, "logGrowth > 0") #0.22

m_cor_prod_host_direct_b <- brm(Prod ~ N15_Coral + N15_Symbiont + (1|Atoll/Island) + (1|Year), data = uvc_cor_prod, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_cor_prod_host_direct_b)
hypothesis(m_cor_prod_host_direct_b, "N15_Coral > 0") #0.68
hypothesis(m_cor_prod_host_direct_b, "N15_Symbiont > 0") #0.42

# coral growth -> corallivore_productivity

# total

m_cor_prod_growth_total <- brm(Prod ~ log(Growth) + (1|Atoll/Island) + (1|Year), data = uvc_cor_prod, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_cor_prod_growth_total)
hypothesis(m_cor_prod_growth_total, "logGrowth > 0") #0.4

# direct

adjustmentSets(dag,
  exposure = "coral_growth", 
  outcome = "corallivore_productivity",
  effect = "direct")

#{ coral_host_nutrients }

# fitted before

#4. Total and direct sb effects

# total

m_cor_prod_sb_total <- brm(Prod ~ log(Seabird_Biomass_density_prop) + (1|Atoll/Island) + (1|Year), data = uvc_cor_prod, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_cor_prod_sb_total)
hypothesis(m_cor_prod_sb_total, "logSeabird_Biomass_density_prop > 0")

# direct

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "corallivore_productivity",
  effect = "direct")

#{ coral_growth, coral_host_nutrients }

m_cor_prod_sb_direct <- brm(Prod ~ log(Seabird_Biomass_density_prop) + log(Growth) + N15_Coral + (1|Atoll/Island) + (1|Year), data = uvc_cor_prod, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_cor_prod_sb_direct)
hypothesis(m_cor_prod_sb_direct, "logSeabird_Biomass_density_prop > 0") #0.05
hypothesis(m_cor_prod_sb_direct, "logGrowth > 0") #0.13
hypothesis(m_cor_prod_sb_direct, "N15_Coral > 0") #0.94

```

##VI. Omnivores 

```{r direct effect-omni}

# omnivores also include mostly carnivorous fishes that also have limited reliance on plankton-derived nutrients (eg triggerfish and wrasses (R. rectangulus and Thalassoma) but small portion tho (~10%) so no plankton_prod -> omnivore_prod arrow in the DAG

# data

uvc_omni_prod <- uvc %>% 
  filter(Diet == "Omnivore") %>%
  left_join(wc_dat %>% group_by(Island, Atoll, Transect, Year, Seabird_Biomass_density_prop) %>% 
              summarize(Wc = mean(Wc, na.rm = T)), 
            by = c("Island", "Atoll", "Transect", "Seabird_Biomass_density_prop", "Year")) %>% 
  left_join(outcomes_uvc_wide, by = c("Island", "Atoll", "Year", "Transect"))

# 1. detritus production -> omnivore productivity

# total

adjustmentSets(dag,
  exposure = "detritus_production", 
  outcome = "omnivore_productivity",
  effect = "total")

# can't test direct

#{ herbivore_productivity, planktivore_productivity }

m_omni_prod_wc_direct <- brm(Prod ~ log(Wc) + log(Prod_Herbivore) + log(Prod_Planktivore) + (1|Atoll/Island) + (1|Year), data = uvc_omni_prod, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_omni_prod_wc_direct)
hypothesis(m_omni_prod_wc_direct, "logWc > 0") #0.75
hypothesis(m_omni_prod_wc_direct, "logProd_Herbivore > 0")#0.48
hypothesis(m_omni_prod_wc_direct, "logProd_Planktivore > 0") #0.02

# 2. cryptic prey pathways

# crypto_inv_productivity -> omnivore_productivity

adjustmentSets(dag,
  exposure = "crypto_inv_productivity", 
  outcome = "omnivore_productivity",
  effect = "total")

# can't estimate

# 3. turf pathway

# turf nutrients -> omnivore_productivity

adjustmentSets(dag,
  exposure = "turf_nutrients", 
  outcome = "omnivore_productivity",
  effect = "total")

#{ coral_host_nutrients, planktonic_night_nutrients, pom_nutrients }
#{ coral_symbiont_nutrients, pom_nutrients }
#{ seabirds }

prior_omni_prod <- c(
  prior(normal(0, 1), class = "b"),
  prior(exponential(1), class = "sd"),
  prior(exponential(1), class = "shape"))

m_omni_prod_turf_total <- brm(Prod ~ N15_Turf + N15_Symbiont + N15_POM + (1|Atoll/Island) + (1|Year), prior = prior_omni_prod, data = uvc_omni_prod, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_omni_prod_turf_total)
hypothesis(m_omni_prod_turf_total, "N15_Turf > 0") #0.5
hypothesis(m_omni_prod_turf_total, "N15_Symbiont > 0") #0.48
hypothesis(m_omni_prod_turf_total, "N15_POM > 0") #0.49

adjustmentSets(dag,
  exposure = "planktonic_day_nutrients", 
  outcome = "omnivore_productivity",
  effect = "direct")

# can't test

adjustmentSets(dag,
  exposure = "detritus_nutrients", 
  outcome = "omnivore_productivity",
  effect = "total")

#{ planktonic_day_nutrients, planktonic_night_nutrients, turf_nutrients }

m_omni_prod_det_total <- brm(Prod ~ N15_Detritus + N15_Turf + N15_Plankton + N15_Plank_night + (1|Atoll/Island) + (1|Year), prior = prior_omni_prod, data = uvc_omni_prod, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_omni_prod_det_total)
hypothesis(m_omni_prod_det_total, "N15_Detritus > 0") #0.25
hypothesis(m_omni_prod_det_total, "N15_Turf > 0") #0.42
hypothesis(m_omni_prod_det_total, "N15_Plankton > 0") #0.5
hypothesis(m_omni_prod_det_total, "N15_Plank_night > 0") #0.77

#{ coral_host_nutrients, pom_nutrients, turf_nutrients }

adjustmentSets(dag,
  exposure = "planktonic_night_nutrients", 
  outcome = "omnivore_productivity",
  effect = "total")

#{ pom_nutrients }

m_omni_prod_plank_night_total <- brm(Prod ~ N15_POM + N15_Plank_night + (1|Atoll/Island) + (1|Year), prior = prior_omni_prod, data = uvc_omni_prod, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

hypothesis(m_omni_prod_plank_night_total, "N15_Plank_night > 0") #0.48

adjustmentSets(dag,
  exposure = "planktonic_day_nutrients", 
  outcome = "omnivore_productivity",
  effect = "total")

#{ pom_nutrients }

m_omni_prod_plank_day_total <- brm(Prod ~ N15_POM + N15_Plankton + (1|Atoll/Island) + (1|Year), data = uvc_omni_prod, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

hypothesis(m_omni_prod_plank_day_total, "N15_Plankton > 0") #0.55

# 4. total and direct sb effect

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "omnivore_productivity",
  effect = "total")

# {}

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "omnivore_productivity",
  effect = "direct")

#{ detritus_nutrients, planktonic_day_nutrients, planktonic_night_nutrients, turf_nutrients }
#{ detritus_nutrients, planktonic_night_nutrients, pom_nutrients, turf_nutrients }
#{ coral_host_nutrients, planktonic_night_nutrients, pom_nutrients, turf_nutrients }
#{ coral_symbiont_nutrients, pom_nutrients, turf_nutrients }

m_omni_prod_sb_direct <- brm(Prod ~ log(Seabird_Biomass_density_prop) + N15_Detritus + N15_Plank_night + N15_Plankton + N15_Turf + (1|Atoll/Island) + (1|Year), data = uvc_omni_prod, prior = prior_omni_prod, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_omni_prod_sb_direct)
hypothesis(m_omni_prod_sb_direct, "N15_Detritus > 0") #0.49
hypothesis(m_omni_prod_sb_direct, "N15_Turf > 0") #0.52
hypothesis(m_omni_prod_sb_direct, "N15_Plank_night > 0") #0.77
hypothesis(m_omni_prod_sb_direct, "N15_Plankton > 0") #0.6
hypothesis(m_omni_prod_sb_direct, "logSeabird_Biomass_density_prop > 0") #0.23

```

##VII. Carnivores 

```{r direct effect-carn}

# data

uvc_carn_prod <- uvc %>% 
  filter(Diet == "Carnivore") 

# 1. crypto_fish_productivity -> carnivore_productivity

# total

adjustmentSets(dag,
  exposure = "crypto_fish_productivity", 
  outcome = "carnivore_productivity",
  effect = "direct")

#{ crypto_inv_productivity }

m_carn_prod_fish_prod_total <- brm(Prod ~ log(Prod_Crypto_fish) + log(Prod_Crypto_inv) + (1|Atoll/Island) + (1|Year), data = uvc_carn_prod, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_carn_prod_fish_prod_total)
hypothesis(m_carn_prod_fish_prod_total, "logProd_Crypto_fish > 0") #0.94
hypothesis(m_carn_prod_fish_prod_total, "logProd_Crypto_inv > 0") #0.53

# direct = total

adjustmentSets(dag,
  exposure = "crypto_inv_productivity", 
  outcome = "carnivore_productivity",
  effect = "direct")

# 3. total and direct sb effect

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "carnivore_productivity",
  effect = "direct")

#{ crypto_fish_productivity, crypto_inv_productivity }

m_carn_prod_sb_direct <- brm(Prod ~ log(Seabird_Biomass_density_prop) + log(Prod_Crypto_fish) + log(Prod_Crypto_inv) +  (1|Atoll/Island) + (1|Year), data = uvc_carn_prod, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_carn_prod_sb_direct)
hypothesis(m_carn_prod_sb_direct, "logSeabird_Biomass_density_prop > 0") #0.33
hypothesis(m_carn_prod_sb_direct, "logProd_Crypto_fish > 0") #0.87
hypothesis(m_carn_prod_sb_direct, "logProd_Crypto_inv > 0") #0.4

```

##VIII. Invertivores

```{r direct effect-inv}

# data

uvc_inv_prod <- uvc %>% 
  filter(Diet == "Invertivore")

# 1. crypto_inv_productivity -> invertivore_productivity

# total

adjustmentSets(dag,
  exposure = "crypto_inv_productivity", 
  outcome = "invertivore_productivity",
  effect = "direct")

#{ }

# direct = total

m_inv_prod_inv_total <- brm(Prod ~ log(Prod_Crypto_inv) + (1|Atoll/Island) + (1|Year), data = uvc_inv_prod, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_inv_prod_inv_total)
hypothesis(m_inv_prod_inv_total, "logProd_Crypto_inv > 0") #0.42

# 2. total and direct sb effect

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "invertivore_productivity",
  effect = "direct")

#{ crypto_inv_productivity }

m_inv_prod_inv_sb_direct <- brm(Prod ~ log(Seabird_Biomass_density_prop) + log(Prod_Crypto_inv) + (1|Atoll/Island) + (1|Year), data = uvc_inv_prod, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_inv_prod_inv_sb_direct)
hypothesis(m_inv_prod_inv_sb_direct, "logProd_Crypto_inv > 0") #0.43
hypothesis(m_inv_prod_inv_sb_direct, "logSeabird_Biomass_density_prop > 0") #0.46

adjustmentSets(dag,
  exposure = "inv_crypto_fish_productivity", 
  outcome = "invertivore_productivity",
  effect = "total")

m_inv_prod_inv_crypto_fish_prod_total <- brm(Prod ~ log(Prod_Inv_crypto_fish) + (1|Atoll/Island) + (1|Year), data = uvc_inv_prod, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

hypothesis(m_inv_prod_inv_crypto_fish_prod_total, "logProd_Inv_crypto_fish > 0") #0.16

m_inv_prod_inv_crypto_fish_prod_direct <- brm(Prod ~ log(Prod_Inv_crypto_fish) + log(Prod_Crypto_inv) + (1|Atoll/Island) + (1|Year), data = uvc_inv_prod, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

hypothesis(m_inv_prod_inv_crypto_fish_prod_direct, "logProd_Inv_crypto_fish > 0") #0.18
hypothesis(m_inv_prod_inv_crypto_fish_prod_direct, "logProd_Crypto_inv > 0") #0.41
```

##IX. Piscivores 

```{r direct effect-pisc}

# data

uvc_pisc_prod <- uvc %>% 
  filter(Diet == "Piscivore") %>% 
  left_join(outcomes_uvc_wide, by = c("Atoll", "Island", "Year", "Transect"))

# 1. crypto_fish_productivity -> carnivore_productivity

# total

adjustmentSets(dag,
  exposure = "crypto_fish_productivity", 
  outcome = "piscivore_productivity",
  effect = "direct")

#total = direct
#{ planktivore_productivity }

m_pisc_prod_fish_prod_total <- brm(Prod ~ log(Prod_Crypto_fish) + log(Prod_Planktivore) + (1|Atoll/Island) + (1|Year), data = uvc_pisc_prod, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_pisc_prod_fish_prod_total)
hypothesis(m_pisc_prod_fish_prod_total, "logProd_Crypto_fish > 0") #0.84
hypothesis(m_pisc_prod_fish_prod_total, "logProd_Planktivore > 0") #0.37

draws_m_pisc_prod_fish_prod_total <- spread_draws(m_pisc_prod_fish_prod_total, b_logProd_Crypto_fish)
doubling_effect_m_pisc_prod_fish_prod_total <- draws_m_pisc_prod_fish_prod_total %>%
  mutate(effect_doubling = exp(b_logProd_Crypto_fish * log(2)))
median(doubling_effect_m_pisc_prod_fish_prod_total$effect_doubling)
hdi(doubling_effect_m_pisc_prod_fish_prod_total$effect_doubling, ci = 0.95)
mean(doubling_effect_m_pisc_prod_fish_prod_total$effect_doubling > 1)

# 2. total and direct sb effect

adjustmentSets(dag,
  exposure = "seabirds", 
  outcome = "piscivore_productivity",
  effect = "direct")

#{ crypto_fish_productivity, planktivore_productivity }

m_pisc_prod_sb_direct <- brm(Prod ~ log(Seabird_Biomass_density_prop) + log(Prod_Crypto_fish) + log(Prod_Planktivore) + (1|Atoll/Island) + (1|Year), data = uvc_pisc_prod, family = Gamma(link = "log"), control = list(adapt_delta = 0.99, max_treedepth = 12))

summary(m_pisc_prod_sb_direct)
hypothesis(m_pisc_prod_sb_direct, "logSeabird_Biomass_density_prop > 0") #0.9
hypothesis(m_pisc_prod_sb_direct, "logProd_Crypto_fish > 0") #0.55
hypothesis(m_pisc_prod_sb_direct, "logProd_Planktivore > 0") #0.23

```
# Inset plots

```{r plot-fig2}

plot.m_symbiont_n15 <- spread_draws(m_symbiont_n15, b_logSeabird_Biomass_density_prop) %>%
  ggplot(aes(y = 0, x = b_logSeabird_Biomass_density_prop, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(clip = "off")

plot.m_symbiont_n15

#ggsave("figures/cor_a.png", plot.m_symbiont_n15, width = 1.5, height = 1, units = "in", dpi = 600)

draws <- spread_draws(m_symbiont_n15, b_logSeabird_Biomass_density_prop)
xlims <- quantile(draws$b_logSeabird_Biomass_density_prop, probs = c(0.001, 0.999))

plot.m_pom_n15 <- draws %>%
  ggplot(aes(y = 0, x = b_logSeabird_Biomass_density_prop, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(xlim = xlims, clip = "off")

#ggsave("figures/cor_b.png", plot.m_pom_n15, width = 1.5, height = 1, units = "in", dpi = 600)

draws <- spread_draws(m_growth_symbiont_direct, b_Symbiont_N15)
xlims <- quantile(draws$b_Symbiont_N15, probs = c(0.01, 0.99))

plot.m_growth_symbiont_direct_Symbiont <- draws %>%
  ggplot(aes(y = 0, x = b_Symbiont_N15, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(xlim = xlims, clip = "off")

#ggsave("figures/cor_c.png", plot.m_growth_symbiont_direct_Symbiont, width = 1.5, height = 1, units = "in", dpi = 600)

draws <- spread_draws(m_plank_night_pom, b_N15_POM)
xlims <- quantile(draws$b_N15_POM, probs = c(0.02, 0.98))

plot.m_plank_night_pom <- draws %>%
  ggplot(aes(y = 0, x = b_N15_POM, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6, adjust = 2) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(xlim = xlims, clip = "off")

plot.m_plank_night_pom

#ggsave("figures/cor_d.png", plot.m_plank_night_pom, width = 1.5, height = 1, units = "in", dpi = 600)

plot.m_host_n15_direct <- spread_draws(m_host_n15_direct, b_Symbiont_N15) %>%
  ggplot(aes(y = 0, x = b_Symbiont_N15, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(clip = "off")

plot.m_host_n15_direct

#ggsave("figures/cor_e.png", plot.m_host_n15_direct, width = 1.5, height = 1, units = "in", dpi = 600)

plot.m_host_n15_plank_night_direct <- spread_draws(m_host_n15_plank_night_direct, b_N15_Plank_night) %>%
  ggplot(aes(y = 0, x = b_N15_Plank_night, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(clip = "off")

#ggsave("figures/cor_f.png", plot.m_host_n15_plank_night_direct, width = 1.5, height = 1, units = "in", dpi = 600)

draws <- spread_draws(m_cor_prod_host_direct, b_logGrowth)
xlims <- quantile(draws$b_logGrowth, probs = c(0.01, 0.99))

plot.m_cor_prod_host_direct_Growth <- draws %>%
  ggplot(aes(y = 0, x = b_logGrowth, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(xlim = xlims, clip = "off")

m_cor_prod_host_direct

#ggsave("figures/cor_g.png", plot.m_cor_prod_host_direct_Growth, width = 1.5, height = 1, units = "in", dpi = 600)

draws <- spread_draws(m_cor_prod_host_direct, b_N15_Coral)
xlims <- quantile(draws$b_N15_Coral, probs = c(0.01, 0.99))

plot.m_cor_prod_host_direct_N15 <- draws %>%
  ggplot(aes(y = 0, x = b_N15_Coral, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(xlim = xlims, clip = "off")

#ggsave("figures/cor_h.png", plot.m_cor_prod_host_direct_N15, width = 1.5, height = 1, units = "in", dpi = 600)


draws <- spread_draws(m_growth_symbiont_direct, b_N15_Plank_night)
xlims <- quantile(draws$b_N15_Plank_night, probs = c(0.01, 0.99))

plot.m_growth_plank_night <- draws %>%
  ggplot(aes(y = 0, x = b_N15_Plank_night, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(xlim = xlims, clip = "off")

#ggsave("figures/cor_i.png", plot.m_growth_plank_night, width = 1.5, height = 1, units = "in", dpi = 600)

draws <- spread_draws(m_growth_symbiont_direct, b_Host_N15)
xlims <- quantile(draws$b_Host_N15, probs = c(0.01, 0.99))

plot.m_growth_symbiont_direct_Host <- draws %>%
  ggplot(aes(y = 0, x = b_Host_N15, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(xlim = xlims, clip = "off")

#ggsave("figures/cor_j.png", plot.m_growth_symbiont_direct_Host, width = 1.5, height = 1, units = "in", dpi = 600)

```

```{r plot-figs4}

draws <- spread_draws(m_turf_n15, b_logSeabird_Biomass_density_prop)
xlims <- quantile(draws$b_logSeabird_Biomass_density_prop, probs = c(0.01, 0.99))

plot.m_turf_n15 <- draws %>%
  ggplot(aes(y = 0, x = b_logSeabird_Biomass_density_prop, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(xlim = xlims, clip = "off")

#ggsave("figures/det_b.png", plot.m_turf_n15, width = 1.5, height = 1, units = "in", dpi = 600) #there was no a in the template


draws <- spread_draws(m_cor_det_n15, b_N15_Coral)
xlims <- quantile(draws$b_N15_Coral, probs = c(0.015, 0.985))

plot.m_cor_det_n15 <- draws %>%
  ggplot(aes(y = 0, x = b_N15_Coral, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(xlim = xlims, clip = "off")

#ggsave("figures/det_c.png", plot.m_cor_det_n15, width = 1.5, height = 1, units = "in", dpi = 600)

plot.m_det_n15_coral_direct <- spread_draws(m_det_n15_coral_direct, b_N15_Coral) %>%
  ggplot(aes(y = 0, x = b_N15_Coral, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(clip = "off")

#ggsave("figures/det_d.png", plot.m_det_n15_coral_direct, width = 1.5, height = 1, units = "in", dpi = 600)

plot.m_det_n15_turf_direct <- spread_draws(m_det_n15_turf_direct, b_N15_Turf) %>%
  ggplot(aes(y = 0, x = b_N15_Turf, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(clip = "off")

#ggsave("figures/det_e.png", plot.m_det_n15_turf_direct, width = 1.5, height = 1, units = "in", dpi = 600)

plot.m_det_n15_pom_direct <- spread_draws(m_det_n15_turf_direct, b_N15_POM) %>%
  ggplot(aes(y = 0, x = b_N15_POM, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(clip = "off")

#ggsave("figures/det_f.png", plot.m_det_n15_pom_direct, width = 1.5, height = 1, units = "in", dpi = 600)

draws <- spread_draws(m_det_n15_cor_det_direct, b_N15_Chaetrif_detritus)
xlims <- quantile(draws$b_N15_Chaetrif_detritus, probs = c(0.025, 0.975))

plot.m_det_n15_cor_det_direct <- draws %>%
  ggplot(aes(y = 0, x = b_N15_Chaetrif_detritus, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(xlim = xlims, clip = "off")

#ggsave("figures/det_g.png", plot.m_det_n15_cor_det_direct, width = 1.5, height = 1, units = "in", dpi = 600)

draws <- spread_draws(m_det_prod_wc, b_N15_Detritus)
xlims <- quantile(draws$b_N15_Detritus, probs = c(0.025, 0.975))

plot.m_det_prod_wc <- draws %>%
  ggplot(aes(y = 0, x = b_N15_Detritus, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(xlim = xlims, clip = "off")

#ggsave("figures/det_h.png", plot.m_det_prod_wc, width = 1.5, height = 1, units = "in", dpi = 600)

plot.m_det_prod_wc_i <- spread_draws(m_det_prod_wc, b_logWc) %>%
  ggplot(aes(y = 0, x = b_logWc, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(clip = "off")

#ggsave("figures/det_i.png", plot.m_det_prod_wc_i, width = 1.5, height = 1, units = "in", dpi = 600)

```

```{r plot-figs5}

plot.m_crypto_inv_prod_inv_crypto_fish_site <- spread_draws(m_crypto_inv_prod_inv_crypto_fish_site, b_logProd_Inv_crypto_fish) %>%
  ggplot(aes(y = 0, x = b_logProd_Inv_crypto_fish, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(clip = "off")

#ggsave("figures/carn_a.png", plot.m_crypto_inv_prod_inv_crypto_fish_site, width = 1.5, height = 1, units = "in", dpi = 600)

draws <- spread_draws(m_carn_prod_fish_prod_total, b_logProd_Crypto_inv)
xlims <- quantile(draws$b_logProd_Crypto_inv, probs = c(0.01, 0.99))

plot.m_carn_prod_fish_prod_total_b <- draws %>%
  ggplot(aes(y = 0, x = b_logProd_Crypto_inv, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(xlim = xlims, clip = "off")

#ggsave("figures/carn_b.png", plot.m_carn_prod_fish_prod_total_b, width = 1.5, height = 1, units = "in", dpi = 600)

draws <- spread_draws(m_carn_prod_fish_prod_total, b_logProd_Crypto_fish)
xlims <- quantile(draws$b_logProd_Crypto_fish, probs = c(0.01, 0.99))

plot.m_carn_prod_fish_prod_total <- draws %>%
  ggplot(aes(y = 0, x = b_logProd_Crypto_fish, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(xlim = xlims, clip = "off")

plot.m_carn_prod_fish_prod_total

#ggsave("figures/carn_c.png", plot.m_carn_prod_fish_prod_total, width = 1.5, height = 1, units = "in", dpi = 600)

draws <- spread_draws(m_inv_prod_inv_total, b_logProd_Crypto_inv)
xlims <- quantile(draws$b_logProd_Crypto_inv, probs = c(0.01, 0.99))

plot.m_inv_prod_inv_total <- draws %>%
  ggplot(aes(y = 0, x = b_logProd_Crypto_inv, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(xlim = xlims, clip = "off")

#ggsave("figures/carn_d.png", plot.m_inv_prod_inv_total, width = 1.5, height = 1, units = "in", dpi = 600)

draws <- spread_draws(m_pisc_prod_fish_prod_total, b_logProd_Crypto_fish)
xlims <- quantile(draws$b_logProd_Crypto_fish, probs = c(0.01, 0.99))

plot.m_pisc_prod_fish_prod_total <- draws %>%
  ggplot(aes(y = 0, x = b_logProd_Crypto_fish, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(xlim = xlims, clip = "off")

#ggsave("figures/carn_e.png", plot.m_pisc_prod_fish_prod_total, width = 1.5, height = 1, units = "in", dpi = 600)

plot.m_pisc_prod_fish_prod_total_f <- spread_draws(m_pisc_prod_fish_prod_total, b_logProd_Planktivore) %>%
  ggplot(aes(y = 0, x = b_logProd_Planktivore, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6, adjust = 2) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(clip = "off")

#ggsave("figures/carn_f.png", plot.m_pisc_prod_fish_prod_total_f, width = 1.5, height = 1, units = "in", dpi = 600)

plot.m_crypto_inv_prod_sb_total_site <- spread_draws(m_crypto_inv_prod_sb_total_site, b_logSeabird_Biomass_density_prop) %>%
  ggplot(aes(y = 0, x = b_logSeabird_Biomass_density_prop, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(clip = "off")

#ggsave("figures/carn_g.png", plot.m_crypto_inv_prod_sb_total_site, width = 2, height = 1, units = "in", dpi = 600)

plot.m_crypto_fish_prod_sb_total_site <- spread_draws(m_crypto_fish_prod_sb_total_site, b_logSeabird_Biomass_density_prop) %>%
  ggplot(aes(y = 0, x = b_logSeabird_Biomass_density_prop, fill = after_stat(x > 0))) +
  stat_halfeye(point_interval = median_hdci, .width = c(.95, .5), fatten_point = 1, slab_alpha = 0.6) +
  scale_fill_manual(values = c("#e89c81", "#d0e2af")) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme(axis.line = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "transparent"),
        legend.position = "none") + 
  coord_cartesian(clip = "off")

#ggsave("figures/carn_h.png", plot.m_crypto_fish_prod_sb_total_site, width = 2, height = 1, units = "in", dpi = 600)

```

